---
title: "Catchment Variables"
author: "Daniel Thurber"
date: "9/24/2021"
output: pdf_document
---
Initialize script with folder locations, libraries, and variables DF
```{r}
library(zoo, warn.conflicts = F)
library(raster, warn.conflicts = F)
vars.df <- read.csv('C:/Users/Daniel/Documents/Research/O2_variables.csv')
rast.dir <- 'C:/Users/Daniel/Documents/Research/gis_projects/O2_catchments/O2_rasters'
catch.list <- as.character(vars.df$SITE_NO_tx)
```

Add leading zeroes to 7-digit codes.
```{r}
#no inputs necessary
for (i in 1:length(catch.list)) {
  if (nchar(catch.list[i])<8){
    catch.list[i] <- paste0("0",catch.list[i])
  }
}
catch.list[65:68]
```

Enter the feature ID of the catchment to analyze
```{r}
FID <- 1
x <- FID +1 #DF row for that catchment
gage.code <- catch.list[x]
paste(gage.code, vars.df$STANAME[x])
vars.df$coName[x]
Eraster <- paste0('E_',gage.code, '.tif')
Araster <- paste0('A_',gage.code, '.tif')
Hraster <- paste0('H_',gage.code, '.tif')
Sraster <- paste0('S_',gage.code,'.tif')
```
(optional) Run this chunk if you need to add a common name for plots
```{r}
vars.df$coName[x] <- 'Rio Lucero'
```

User input - name and elevation of snotel site for plots
```{r}
catchment <- vars.df$coName[x]  #full river name to display in plots

st1 <- 'Taos Powderhorn' #snotel station name for plots+
st1el <- 11057*.3048  #elevations in feet: multiply by 0.3048 ft/m

```

```{r}
DEM <- raster(paste0(rast.dir,'/',Eraster))
aspect <- raster(paste0(rast.dir,'/',Araster))
HillShade <- raster(paste0(rast.dir,'/',Hraster))
elevFreq <- freq(DEM)
```

```{r}
dem.df <- na.omit(as.data.frame(DEM))
a.df <- na.omit(as.data.frame(aspect))
a.df[(which(a.df[,1]==-1)),1] <- NA  #replace level pixels (A = -1) with NA
a.df$sin <- sin(a.df[,1]*pi/180)
a.df$cos <- cos(a.df[,1]*pi/180)

hs.df <- na.omit(as.data.frame(HillShade))
```

```{r}
sinMean <- mean(a.df$sin, na.rm = T)
cosMean <- mean(a.df$cos, na.rm = T)
aspMean <- atan(sinMean/cosMean)/pi*180
if(sinMean<0 & cosMean>0){
  aspMean <- aspMean+360}
if(cosMean<0){
  aspMean <- aspMean+180
}
paste('Mean aspect:',aspMean)
```


```{r}
hsMean <- mean(hs.df[,1], na.rm = T)
paste('Mean hillshade:', hsMean)
```
```{r}
elevMean <- mean(dem.df[,1], na.rm = T)
paste('Mean elevation:', elevMean)
```


View the elevFreq dataframe.  If there are rows for zero or negative values, remove them.
```{r}
head(elevFreq,3)
tail(elevFreq,3)
st1el
```


Create a dataframe with frequencies of all elevation values and cumulative sums
```{r}
truelev <- data.frame(elevFreq[c(1:(nrow(elevFreq)-1)),]) #ignores last row with NA values
#truelev <- data.frame(elevFreq[-c(1,2),]) #use this to remove any rows
for (i in seq(1,nrow(truelev))){
  truelev$sum[i] <- sum(truelev$count[1:i])
}

truelev$CDVal <- truelev$sum/sum(truelev$count)
tail(truelev,2) #last two lines should approach and equal 1 for CDVal
```

Determine and look at the total range of elevations
```{r}
minelev <- min(truelev$value)
maxelev <- max(truelev$value)
elevrange <- maxelev - minelev
minelev
maxelev
elevrange
```
Generate a column of elevation proportion and determine hypsometric integral and median elevation
```{r}
truelev$elevprop <- (truelev$value-minelev)/elevrange
head(truelev,3)
tail(truelev,3)
HI <- sum(truelev$count*truelev$elevprop)/sum(truelev$count) #determines hypsometric integral
medElev <- truelev$value[which(truelev$CDVal>0.5)[1]] #displays the median
paste('Hypsometric Integral:', HI, '; median elevation (m):', medElev)
paste('mean elevation:', elevMean)

```

```{r}
plot(truelev$CDVal~truelev$value, 
     xlab = 'Elevation', 
     ylab = "Cumulative Percent", 
     main = paste0('Cumulative Elevation Distribution for ', catchment), 
     type = 'l')
abline(v = st1el, col = 'darkolivegreen4')
#abline(v = st2el, col = 'lightsalmon2')
legend('bottomright', inset = .05, lty = 1, legend = c(st1), col = c('darkolivegreen4'), title = 'SnoTel Sites')
```
```{r}
snoelevCDF <- truelev$CDVal[which(truelev$value==round(st1el))]
snoelevCDF
```


The next section generates a smoothed PDF plot of the elevation distribution

---

```{r}
truelev$local11 <- c(NA,NA,NA,NA,NA,rollmean(truelev$count,11),NA,NA,NA,NA,NA)
```





```{r}
plot((truelev$count/sum(truelev$count))~truelev$value,
     xlab = 'Elevation',
     ylab = "Cumulative Percent",
     main = paste0('Relative Elevation Distribution for ', catchment),
     type = "l")

```



```{r}
plot((truelev$local11/sum(truelev$count))~truelev$value,
     xlab = 'Elevation',
     ylab = "Relative Percent",
     main = paste0('Relative Elevation Distribution for ', catchment),
     type = "l")
abline(v = st1el, col = 'darkolivegreen4')
#abline(v = st2el, col = 'lightsalmon2')
legend('topleft', inset = .05, lty = 1, legend = c(st1), col = c('darkolivegreen4','lightsalmon2'), title = 'SnoTel Sites')

```

---

Make sure you are still looking at the right catchment and all catchment variables have been calculated:
```{r}
paste(gage.code, vars.df$coName[x])
HI
hsMean
elevMean
medElev
aspMean
snoelevCDF
```


```{r}
vars.df$hypInt[x] <- HI
vars.df$hsMean[x] <-hsMean
vars.df$elevMean[x] <- elevMean
vars.df$elevMed[x] <- medElev
vars.df$aspMean[x] <- aspMean
vars.df$snoelevCDF[x] <- snoelevCDF
vars.df[seq(x-1,x+1),]
```


```{r}
write.csv(vars.df, 'C:/Users/Daniel/Documents/Research/O2_variables.csv')
```

