---
title: "Correlograms"
author: "Daniel Thurber"
date: "5/7/2021"
output: pdf_document
---
```{r}
mypath <- 'C:/Users/Daniel/Documents/Research/data/dataframes/'  #leave this as directory
library(ggplot2)
library(naniar)
sitecodes <- c('LR_FB_BA', 'LR_TG_BA', 'BC_CONF_A', 'TF_CONF_A', 'RHF_CONF_A', 
               'RS_CONF_A')
sitenames <- c('Franklin Basin', 'Tony Grove', 'Beaver Creek', 'Temple Fork', 'Right Hand Fork', 
               'Ricks Spring')
i <- 1
snofile <- 'KN_1115.csv'
site <- sitecodes[i]               #enter site code for file upload and export
sitename <- sitenames[i]        #enter site name for plotting
paste('Site:', sitecodes[i], '-', sitenames[i])
linecols <- c('brown3', 'goldenrod', 'forestgreen', 'bisque4', 'slateblue', 'sienna3', 'aquamarine3', 'magenta4')
#color vector gets used by other plotting scripts.  Attempt to maintain any changes made to the palette
```

Begin by running SNOTEL and LRO_aquatic scripts to generate the qtc and snodf dataframes as .csv files.  This chunk will re-open them.

```{r}
qtc <- read.csv(paste0(mypath,site,'.csv'), stringsAsFactors = F)
snodf <- read.csv(paste0(mypath,snofile), stringsAsFactors = F)
qtc$date <- as.Date(qtc$date,'%Y-%m-%d')
snodf$Date = as.Date(snodf$Date, format = '%Y-%m-%d')
mindate <- qtc$date[1]
```



Calculate autocorrelation functions for each variable and compile in DF
```{r}
lagmax <- 360
Qacf <- acf(qtc$discharge, lag.max = lagmax, type = "correlation", plot = F, na.action = na.pass)
Tacf <- acf(qtc$temperature, lag.max = lagmax, type = "correlation", plot = F, na.action = na.pass)
Cacf <- acf(qtc$conductance, lag.max = lagmax, type = "correlation", plot = F, na.action = na.pass)

acfdf <- data.frame('lag' = Cacf$lag, 
                    'Qval' = c(Qacf$acf, rep(NA,times = lagmax+1-length(Qacf$acf))), #adds NA to missing values
                    'Tval' = Tacf$acf, 
                    'Cval' = Cacf$acf)

```

Plot autocorrelation functions for Q, EC, and T at a given site
```{r}
plot(acfdf$lag, acfdf$Qval, type = 'l', col='blue',
     ylab = 'Correlation', xlab = 'Lag', ylim = c(-1,1), main = paste('Autocorrelation functions for' ,sitename))
lines(acfdf$Tval, col = 'brown4')
lines(acfdf$Cval, col = 'green')
legend(155,1, legend = c('discharge', 'conductance', 'temperature'), 
       lty = 1, col = c('blue', 'green', 'brown4'))

```
Show the date range of the dataframe
```{r}
paste(min(qtc$WY), 'through', max(qtc$WY))
```

select a specific water year, display the lines with 
```{r}
wateryear <- 2018
wydf <- qtc[which(qtc$WY==wateryear),]
paste('Missing discharge:')
which(is.na(wydf$discharge))
paste('Missing conductance:')
which(is.na(wydf$conductance))
nrow(wydf)
```

```{r}
plot(wydf$discharge[235:360], type = 'l')
```

Based on the missing values, identify an interval over which to evaluate the autocorrelation function
```{r}
lagmax <- 50  #this should be left at 50
Qstart <- 1   #first day of extended Q records
Qend <- 200  #last day of Q records
Cstart <- 1   #first day of extended SC records
Cend <- 279   #last day of SC records
wyQacf <- acf(wydf$discharge[Qstart:Qend], lag.max = lagmax, type = "correlation", plot = F, na.action = na.pass)
#wyTacf <- acf(wydf$temperature[Cstart:acfend], lag.max = lagmax, type = "correlation", plot = F, na.action = na.pass)
wyCacf <- acf(wydf$conductance[Cstart:Cend], lag.max = lagmax, type = "correlation", plot = F, na.action = na.pass)

wyacfdf <- data.frame('lag' = wyCacf$lag, 
                    'Qval' = wyQacf$acf, #adds NA to missing values
                     
                    'Cval' = wyCacf$acf)
qdates <- paste('Q:',format(wydf$date[Qstart], '%m/%d'), 'through' ,format(wydf$date[Qend], '%m/%d'))
cdates <- paste('C:',format(wydf$date[Cstart], '%m/%d'), 'through' ,format(wydf$date[Cend], '%m/%d'))
paste(qdates,'    ', cdates)
```

Create a plot for the particular water year.  Add any relevant notes about the timeframe over which this was evaluated
```{r}
plot(wyacfdf$lag, wyacfdf$Qval, type = 'l', col='blue',
     ylab = 'Correlation', xlab = 'Lag', ylim = c(0,1),
     main = paste('Autocorrelation functions for' ,sitename, wateryear))
lines(wyacfdf$Cval, col = 'green')
legend('topright', legend = c('discharge', 'conductance'), 
       lty = 1, col = c('blue', 'green'))
abline(h = .2, lty = 4)
text(x = 40, y =0.7, labels = qdates)
#text(x = 40, y =0.7, labels = 'Discharge missing 1/06')
text(x = 40, y =0.6, labels = cdates)
text(x = 40, y = 0.5, labels = paste('Q:', which(wyacfdf$Qval<0.2)[1], 'days'))
text(x = 40, y = 0.4, labels = paste('SC:', which(wyacfdf$Cval<0.2)[1], 'days'))

```





This chunk will compile a dataframe with columns for date, melt, rain, discharge, temp, and conductance
```{r}
crossdf <- data.frame(date = snodf$Date[which(snodf$Date==mindate):nrow(snodf)])
crossdf$melt = snodf$melt[which(snodf$Date==mindate):nrow(snodf)]
crossdf$rain = snodf$rain[which(snodf$Date==mindate):nrow(snodf)]
for (i in 1:nrow(qtc)){
  crossdf$discharge[which(crossdf$date == qtc$date[i])] = qtc$discharge[i]
}
for (i in 1:nrow(qtc)){
  crossdf$conductance[which(crossdf$date == qtc$date[i])] = qtc$conductance[i]
}
for (i in 1:nrow(qtc)){
  crossdf$temp[which(crossdf$date == qtc$date[i])] = qtc$temperature[i]
}
crossdf$SWI <- crossdf$melt+crossdf$rain
```

Generate CCF objects for each relationship we are interested in:
```{r}
c_by_m <- ccf(crossdf$conductance,crossdf$melt, lag.max = lagmax, plot = F)
q_by_t <- ccf(crossdf$discharge,crossdf$temp, lag.max = lagmax, plot = F)
q_by_c <- ccf(crossdf$discharge,crossdf$conductance, lag.max = lagmax, plot = F)
q_by_m <- ccf(crossdf$discharge,crossdf$melt, lag.max = lagmax, plot = F)
q_by_r <- ccf(crossdf$discharge,crossdf$rain, lag.max = lagmax, plot = F, na.action = na.pass)
q_by_swi <- ccf(crossdf$discharge,crossdf$SWI, lag.max = lagmax, plot = F, na.action = na.pass)
t_by_c <- ccf(crossdf$temp,crossdf$conductance, lag.max = lagmax, plot = F)
```

Create on plot of all calculated cross-correlations
```{r}
par( mar = c(5.1,4.1,4.1,8.1))
plot(c_by_m$acf~c_by_m$lag, xlab='lag (days)', ylab='correlation',
     col=linecols[1], type = 'l', ylim=c(-0.4,0.4), xlim = c(0,lagmax))
lines(q_by_t$acf, col=linecols[2])
lines(q_by_c$acf, col = linecols[3])
lines(q_by_m$acf, col = linecols[4])
lines(q_by_swi$acf, col = linecols[5])
lines(t_by_c$acf, col = linecols[6])
lines(q_by_r$acf, col = linecols[7])

par(xpd=T)
title(main = c("Cross-correlation function for",sitename))
legend('topright', col = linecols, lty = 1, inset = c(-.3,0),
       legend = c('ec | melt', 'Q | T', 'Q | ec', 'Q | melt', 'Q | SWI', 'T | ec', 'Q | rain'))
```
```{r}
corrhold <- 0.20
paste('Lag times for end of correlation at',sitename)
paste('Discharge:',acfdf$lag[which(acfdf$Qval<corrhold)[1]])
paste('Conductivity:',acfdf$lag[which(acfdf$Cval<corrhold)[1]])
paste('Q | melt peaks after', q_by_m$lag[which(q_by_m$acf==max(q_by_m$acf[362:462]))] ,
      'days at', max(q_by_m$acf[362:462]))
paste('SC | melt peaks after', c_by_m$lag[which(c_by_m$acf==min(c_by_m$acf[362:462]))] ,
      'days at', min(c_by_m$acf[362:462]))
paste('Q | SC peaks after', q_by_c$lag[which(q_by_c$acf==min(q_by_c$acf[362:462]))] ,
      'days at', min(q_by_c$acf[362:462]))
```
Run this chunk to explore correlation values and timing for Q | melt
```{r}
poslag <- which(q_by_m$lag>0)
poslag[1]
q_by_m$acf[362:462]
q_by_m$lag[which(abs(q_by_m$acf)>0.20)]

```
```{r}
poslag <- which(c_by_m$lag>0)
poslag[1]
c_by_m$acf[362:462]
c_by_m$lag[which(abs(c_by_m$acf)>0.20)]
```

```{r}
plot(c_by_m$acf~q_by_m$lag, type = 'l')
q_by_c$acf[362:462]
```

Plot multiple relevant/interesting correlograms together
```{r}
lagdays <- 80
plot(acfdf$lag, acfdf$Qval, type = 'l', col='cadetblue4',
     ylab = 'Correlation', xlab = 'Lag', ylim = c(0.2,1), xlim=c(0,lagdays),
     main = paste('Mixed correlation functions for' ,sitename))
lines(acfdf$Cval, col = 'palegreen4')
lines(q_by_m$acf, col = 'brown4')
lines(-1*c_by_m$acf, col = linecols[1] )
legend('topright', legend = c('Q acf', 'SC acf', 'Q | melt', 'C | melt'), 
       lty = 1, col = c('cadetblue4', 'palegreen4', 'brown4', linecols[1]))

```

