---
title: "LRO Time Series"
author: "Daniel Thurber"
date: "1/18/2021"
output: pdf_document
---

```{r}
mypath <- 'C:/Users/Daniel/Documents/Research/data/dataframes/'  #leave this as directory
library(ggplot2)
library(naniar)
library(tidyverse)

sitecodes <- c('LR_FB_BA', 'LR_TG_BA', 'BC_CONF_A', 'TF_CONF_A','RHF_CONF_A', 'RS_CONF_A', 
               'TF_SAWM_A', 'SPC_CONF_A', 'LR_WC_A', 'LR_GCB_A', 'WCS_CONF_A', 'LR_FD')
sitenames <- c('Franklin Basin', 'Tony Grove', 'Beaver Creek', 'Temple Fork', 'Right Hand Fork','Ricks Spring', 
               'TF at Sawmill', 'Spawn Creek', 'Above Wood Camp', 'Guinavah Campground','Wood Camp Spring','First Dam')
siteabbr <- c('FB', 'TG', 'BC', 'TF','RH', 'RS', 
              'TS', 'SC', 'WC', 'GC', 'WS','FD')
i <- 1
site <- sitecodes[i]               #enter site code for file upload and export
sitename <- sitenames[i]        #enter site name for plotting
paste('Site:', sitecodes[i], '-', sitenames[i])
   #the line color vector is used by other plotting scripts as well.  Attempt to keep it consistent
linecols <- c('brown3', 'goldenrod', 'forestgreen', 'bisque4', 'slateblue', 'tan1', 
              'aquamarine3', 'magenta4', 'sienna3','cyan','violetred2','yellow2')
linetypes <- c(1,1,1,1,1,3,1,1,1,1,4,1)
rgbmat <- col2rgb(linecols)
```

Initialize catchment areas in km^2
```{r}
site.areas <- c(65.9767, #FB
                277.965, #TG
                103.4015, #BC
                41.4076, #TF
                65.1986, #RH
                NA, #RS
                8.6085, #TS
                14.7168, #SC
                403.874, #WC
                520.8331, #GC
                NA, #WS
                554 #FD
                )
```

Take a look at the color palette, adjust if desired
```{r, fig.height=1.5, fig.width=7}
linecols <- c('brown3', 'goldenrod', 'forestgreen', 'bisque4', 'slateblue', 'tan1', 
              'aquamarine3', 'magenta4', 'sienna3','cyan','violetred2','yellow2')
par(mar = c(4,0,0,0))
image(1:length(linecols),.1, as.matrix(1:length(linecols)), col = linecols, yaxt = 'n', ylab = '', xlab = 'catchment', xaxt = 'n')
axis(side = 1, at = 1:length(linecols), labels = siteabbr)
```

### plot discharge, conductance, and temperature time series by water year for a selected site
Read the given csv into a dataframe.
```{r}
qtc <- read.csv(paste0(mypath,site,'.csv'), stringsAsFactors = F)
```


format date as a date and generate day column without year, then check the data formats. 
```{r}

qtc$date <- as.Date(qtc$date,'%Y-%m-%d')
qtc$day <- format(as.Date(qtc$date),'%m-%d')
qtc$wyday <- 0
head(qtc,3)
```

create a reference dataframe relating water year days to month-day format
```{r}
wydates <- data.frame(wyday = seq(1,366),
day=format(seq.Date(as.Date('2019-10-1','%Y-%m-%d'),as.Date('2020-09-30','%Y-%m-%d'),1),'%m-%d'))
```


Populate water year day column with appropriate values 1-366
```{r}
for (i in 1:nrow(qtc)){
  qtc$wyday[i] <- wydates$wyday[which(wydates$day==qtc$day[i])]
}
```

Set viewing parameters and generate a discharge plot

```{r}
xrange <- c(1,366)   #range of water year days to consider
dayticks <- 11 #number of tick marks on x axis
yrange <- c(min(qtc$discharge, na.rm = T), max(qtc$discharge, na.rm = T))
#yrange <- c(0,10)  #un-comment to set custom y-axis
pltyears <- seq(min(qtc$WY),max(qtc$WY))
#pltyears <- c(2015,2017,2019)  #un-comment to select custom year range

wylabels <- wydates$day[seq(xrange[1],xrange[2],length.out = dayticks)]
plot(qtc$wyday[which(qtc$WY==pltyears[1])],qtc$discharge[which(qtc$WY==pltyears[1])], type = 'l', 
#     xlim = xrange, 
      ylim = yrange, 
     xlim = c(170,290),
     xaxt = 'n',
     xlab = 'Day of Year', ylab = 'Discharge (cms)', col = linecols[1],
     main = paste('Discharge of ', sitename, ' by water year'))
axis(1, at = seq(xrange[1],xrange[2],length.out = dayticks), labels = wylabels)
for (i in 2:length(pltyears)){
  lines(qtc$wyday[which(qtc$WY==pltyears[i])],qtc$discharge[which(qtc$WY==pltyears[i])],col = linecols[i])
}
legend('topleft', legend = pltyears, lty = 1, col = linecols)
```

Set viewing parameters and generate a temperature plot

```{r}
xrange <- c(1,366)   #range of water year days to consider, 1 to 366
dayticks <- 8 #number of tick marks on x axis
yrange <- c(min(qtc$temperature, na.rm = T), max(qtc$temperature, na.rm = T))
#yrange <- c(0,10)  #un-comment to set custom y-axis
pltyears <- seq(min(qtc$WY),max(qtc$WY))
#pltyears <- c(2015,2019)  #un-comment to select custom year range

wylabels <- wydates$day[seq(xrange[1],xrange[2],length.out = dayticks)]
plot(qtc$wyday[which(qtc$WY==pltyears[1])],qtc$temperature[which(qtc$WY==pltyears[1])], type = 'l', 
     xlim = xrange, ylim = yrange, xaxt = 'n',
     xlab = 'Day of Year', ylab = 'Temperature (deg C)', col = linecols[1],
     main = paste('Temperature of ', sitename, ' by water year'))
axis(1, at = seq(xrange[1],xrange[2],length.out = dayticks), labels = wylabels)
for (i in 2:length(pltyears)){
  lines(qtc$wyday[which(qtc$WY==pltyears[i])],qtc$temperature[which(qtc$WY==pltyears[i])],col = linecols[i])
}
legend('topleft', legend = pltyears, lty = 1, col = linecols)
```


Set viewing parameters and generate a specific conductance plot

```{r}
xrange <- c(1,366)   #range of water year days to consider
dayticks <- 11 #number of tick marks on x axis
yrange <- c(min(qtc$conductance, na.rm = T), max(qtc$conductance, na.rm = T))
#yrange <- c(0,10)  #un-comment to set custom y-axis
pltyears <- seq(min(qtc$WY),max(qtc$WY))
#pltyears <- c(2015,2018)  #un-comment to select custom year range

wylabels <- wydates$day[seq(xrange[1],xrange[2],length.out = dayticks)]
plot(qtc$wyday[which(qtc$WY==pltyears[1])],qtc$conductance[which(qtc$WY==pltyears[1])], type = 'l', 
     xlim = xrange, ylim = yrange, xaxt = 'n',
     xlab = 'Day of Year', ylab = 'conductance (uS/cm)', col = linecols[1],
     main = paste('Specific conductance of ', sitename, ' by water year'))
axis(1, at = seq(xrange[1],xrange[2],length.out = dayticks), labels = wylabels)
for (i in 2:length(pltyears)){
  lines(qtc$wyday[which(qtc$WY==pltyears[i])],qtc$conductance[which(qtc$WY==pltyears[i])],col = linecols[i])
}
legend('bottomleft', legend = pltyears, lty = 1, col = linecols)
```

Define a water year and plot temp and conductivity together
```{r}
pltyear <- 2019
xrange <- c(150,300)   #range of water year days to consider
dayticks <- 11 #number of tick marks on x axis
yrange <- c(min(qtc$conductance, na.rm = T), max(qtc$conductance, na.rm = T))
yrange <- c(250,420)  #un-comment to set custom y-axis

wylabels <- wydates$day[seq(xrange[1],xrange[2],length.out = dayticks)]
plot(qtc$wyday[which(qtc$WY==pltyear)],qtc$conductance[which(qtc$WY==pltyear)], type = 'l', 
     xlim = xrange, ylim = yrange, xaxt = 'n',
     xlab = 'Day of Year', ylab = 'conductance (uS/cm)', col = linecols[1],
     main = paste('SC and Temp of ', sitename, 'for water year', pltyear))
axis(1, at = seq(xrange[1],xrange[2],length.out = dayticks), labels = wylabels)

legend('bottomleft', legend = c('conductance', 'temp'
), lty = 1, col = linecols)

par(new = T)
plot(qtc$temperature[which(qtc$WY==pltyear)], 
     xlab = '', ylab = '',
     col=linecols[2], type = 'l', axes= F)
axis(side = 4, at = pretty(range(qtc$temperature)))      # Add second axis
mtext("water temp (C)", side = 4, line = 3)
```



Define a water year and plot discharge and conductivity together
```{r}
wy <- 2020
wydf <- qtc[which(qtc$WY == wy),]
xrange <- c(1,365)   #range of water year days to consider
dayticks <- 11 #number of tick marks on x axis
yrange <- c(min(wydf$conductance, na.rm = T), max(wydf$conductance, na.rm = T))
#yrange <- c(250,420)  #un-comment to set custom y-axis
mean(qtc$discharge[which(qtc$WY == wy)], na.rm = T)
```

```{r}
wylabels <- wydates$day[seq(xrange[1],xrange[2],length.out = dayticks)]
par(mar = c(4,4,2,4.5))
plot(wydf$wyday,wydf$conductance, type = 'l', 
     xlim = xrange, ylim = yrange, xaxt = 'n',
     xlab = 'Day of Year', ylab = 'conductance (uS/cm)', col = linecols[1],
     main = paste('SC and Discharge of ', sitename, 'for water year', wy))
axis(1, at = seq(xrange[1],xrange[2],length.out = dayticks), labels = wylabels)

legend('left', legend = c('conductance', 'discharge'
), lty = 1, col = linecols)

par(new = T)
plot(wydf$discharge[xrange[1]:xrange[2]], 
     xlab = '', ylab = '',
     col=linecols[2], type = 'l', axes= F)
axis(side = 4, pretty(range(wydf$discharge, na.rm = T),5))      # Add second axis
mtext("discharge", side = 4, line = 3)
```



### plot water year discharge SWIT together
```{r}
i <- 5
site <- sitecodes[i]               #enter site code for file upload and export
sitename <- sitenames[i]        #enter site name for plotting
paste('Site:', sitecodes[i], '-', sitenames[i])
crossdf <- read.csv(paste0('C:/Users/Daniel/Documents/Research/data/dataframes/',site,'_mod.csv'))
paste('date format:', crossdf$date[1])
```
Check the format of the date as printed above and activate the appropriate date formatting line below
```{r}
crossdf$date <- as.Date(crossdf$date,'%Y-%m-%d')
#crossdf$date <- as.Date(crossdf$date,'%m/%d/%Y')
paste('starting date:', crossdf$date[1])
paste('Water years:') 
paste(unique(crossdf$WY))
```

```{r}
plot(crossdf$qpatch~crossdf$date, type = 'l')
plot(crossdf$SWIT~crossdf$date, type = 'l')

```


Generate a dataframe for a selected year, caculate total SWIT for that year
```{r}
wateryear <- 2018
wydf <- crossdf[which(crossdf$WY==wateryear),]
sum(wydf$SWIT)
```




```{r}
par(mar = c(4,4,4,6))
a <- 124 #index to start plot
b <- 300 #approx one year after a
barplot(wydf$SWIT[a:b], axes = F)
axis(side = 4, at = pretty(range(wydf$SWIT[a:b]), n = 4),main = 'SWIT')
mtext('Surface water input (mm)', side = 4, line = 2)

par(new=T)
yrange = range(wydf$qpatch[a:b], na.rm = T)
#plot discharge over the window.  The line gets plotted later over the highlight rectangles
plot(wydf$qpatch, xlim = c(a, b), ylim = yrange, type = 'l', ylab = 'Discharge (m^3/s)', 
     col = linecols[i],
     main = paste('SWIT & discharge at', sitename,wydf$WY[a]), xaxt = 'n', xlab = 'date'
     )
axis(1, at = seq(a,b, length.out = 6), labels = (wydf$date[seq(a,b,length.out = 6)]))


```
```{r}
par(mar = c(4,4,4,6))
a <- 124 #index to start plot
b <- 300 #approx one year after a
barplot(wydf$SWI[a:b], axes = F)
axis(side = 4, at = pretty(range(wydf$SWI[a:b]), n = 4),main = 'SWI')
mtext('Surface water input (mm)', side = 4, line = 2)

par(new=T)
yrange = range(wydf$qpatch[a:b], na.rm = T)
#plot discharge over the window.  The line gets plotted later over the highlight rectangles
plot(wydf$qpatch, xlim = c(a, b), ylim = yrange, type = 'l', ylab = 'Discharge (m^3/s)', 
     col = linecols[i],
     main = paste('SNOTEL-based SWI & discharge at', sitename,wydf$WY[a]), xaxt = 'n', xlab = 'date'
     )
axis(1, at = seq(a,b, length.out = 6), labels = (wydf$date[seq(a,b,length.out = 6)]))


```


```{r}
par(mar = c(4,4,4,6))
a <- 124 #index to start plot
b <- 300 #approx one year after a
barplot(wydf$SWIT[a:b], axes = F)
axis(side = 4, at = pretty(range(wydf$SWIT[a:b]), n = 4),main = 'SWIT')
mtext('Surface water input (mm)', side = 4, line = 2)

par(new=T)
#plot discharge over the window.  The line gets plotted later over the highlight rectangles
plot(wydf$qpatch*3.6/site.areas[i], xlim = c(a, b), ylim = c(0,0.05), type = 'l', ylab = 'Discharge (mm/hr)', 
     col = linecols[i],
     main = paste('SWIT & normalized discharge at', sitename,wydf$WY[a]), xaxt = 'n', xlab = 'date'
     )
axis(1, at = seq(a,b, length.out = 6), labels = (wydf$date[seq(a,b,length.out = 6)]))


```

### plot aquatic variable for multiple sites within a selected water year
--- import, prepare, and filter dataframe for all sites
```{r}
all.sites <-  read.csv('C:/Users/Daniel/Documents/Research/data/dataframes/all_LRO_sites.csv')
all.sites$date <- as.Date(all.sites$date,'%m/%d/%Y')
class(all.sites$date)
colnames(all.sites)
```

Add water year columns to dataframe
```{r}
all.sites$day <- format(as.Date(all.sites$date, '%m/%d/%Y'),'%m-%d')
all.sites$wyday <- 0
all.sites$WY <- NA

wydates <- data.frame(wyday = seq(1,366),
day=format(seq.Date(as.Date('2019-10-1','%Y-%m-%d'),as.Date('2020-09-30','%Y-%m-%d'),1),'%m-%d'))

for (i in 1:nrow(all.sites)){
  all.sites$wyday[i] <- wydates$wyday[which(wydates$day==all.sites$day[i])]
}

all.sites$WY = ifelse(as.numeric(format(all.sites$date,'%m'))>=10, 
                     as.numeric(format(all.sites$date,'%Y'))+1, 
                     as.numeric(format(all.sites$date,'%Y')))

colnames(all.sites)
paste(class(all.sites$date), all.sites$date[1])
```
Select water year and variable of interest, restrict dataframe by water year
```{r}
water.year <- 2019
variable <- "CP"
wy.df <- all.sites[which(all.sites$WY==water.year),]
```

identify columns to keep (no user input)
```{r}
sel.codes <- colnames(wy.df)

date.cols <- which(colnames(wy.df) %in% c('date', 'day', 'wyday','WY'))
sel.codes[date.cols]

sel.cols <- which(str_sub(sel.codes,4,5)==variable)
sel.codes[sel.cols]
paste(length(sel.cols), 'sites')
```

Filter dataframe with only selected columns
```{r}
wy.df <- wy.df[c(date.cols,sel.cols)]
date.cols <- NULL
sel.cols <- NULL

```


--- plot area-Normalized discharge
```{r}
choices <- c(1,3,4,5,7,8,12)
site.choices <- siteabbr[choices]

plot.cols <- which(substr(colnames(wy.df),1,2) %in% site.choices)

na.check = rep(NA,length(plot.cols))
for(i in 1:length(plot.cols)){
  na.check[i] <- sum(is.na(wy.df[,plot.cols[i]]))
}

data.frame('sites'=site.choices,'ID' = choices, 'column' = plot.cols, 'NA_count' = na.check)

```

```{r}
a <- 120
b <- 320

par(mar = c(4,4,5,6))
plot(wy.df$FB_QP, xaxt = 'n', xlab = 'day', ylab = 'normalized Q (mm/hr)',
     xlim = c(a,b), ylim = c(0, .3),
     main = paste('discharge for Logan subcatchments -', water.year),type = 'n')
axis(1, at = seq(a,b, length.out = 8), labels = (wy.df$day[seq(a,b,length.out = 8)]))

for (i in 1:length(plot.cols)){
  lines(wy.df[,plot.cols[i]]/site.areas[choices[i]]*3.6, col = linecols[choices[i]], lty = linetypes[choices[i]])
}

#lines(wy.df$FB_QP*3.6/site.areas[1], col = linecols[1])




legend('right', inset = -0.2, legend = site.choices, lty = linetypes[choices], col = linecols[choices], xpd = T)
```

Plot each relative to the discharge of first dam

```{r}
a <- 120
b <- 320

par(mar = c(4,4,5,6))
plot(wy.df$FB_QP, xaxt = 'n', xlab = 'day', ylab = 'normalized Q (mm/hr)',
     xlim = c(a,b), ylim = c(0, 5),
     main = paste('Relative response for Logan subcatchments -', water.year),type = 'n')
axis(1, at = seq(a,b, length.out = 8), labels = (wy.df$day[seq(a,b,length.out = 8)]))

for (i in 1:length(plot.cols)){
  lines(wy.df[,plot.cols[i]]/site.areas[choices[i]]/(wy.df$FD_QP/site.areas[12]), col = linecols[choices[i]], lty = linetypes[choices[i]])
}

#lines(wy.df$FB_QP*3.6/site.areas[1], col = linecols[1])




legend('right', inset = -0.2, legend = site.choices, lty = linetypes[choices], col = linecols[choices], xpd = T)
```


--- plot peak-normalized discharge
```{r}
choices <- c(2,6,9,11)
site.choices <- siteabbr[choices]

plot.cols <- which(substr(colnames(wy.df),1,2) %in% site.choices)

na.check = rep(NA,length(plot.cols))
for(i in 1:length(plot.cols)){
  na.check[i] <- sum(is.na(wy.df[,plot.cols[i]]))
}

data.frame('sites'=site.choices,'ID' = choices, 'column' = plot.cols, 'NA_count' = na.check)

```

```{r}
a <- 170
b <- 280
par(mar = c(4,4,5,6))
plot(wy.df$FB_QP, xaxt = 'n', xlab = 'day', ylab = 'discharge (relative peak)',xlim = c(a,b), ylim = c(0, 1),
     main = paste('Discharge for Logan subcatchments -', water.year),type = 'n')
axis(1, at = seq(a,b, length.out = 8), labels = (wy.df$day[seq(a,b,length.out = 8)]))

for (i in 1:length(plot.cols)){
  lines(wy.df[,plot.cols[i]]/max(wy.df[,plot.cols[i]], na.rm = T), col = linecols[choices[i]], lty = linetypes[choices[i]])
}

legend('right', inset = -0.2, legend = site.choices, lty = linetypes[choices], col = linecols[choices], xpd = T)
```

--- Baseflow distributions (box plots)
```{r}
sel.day <- 153
wy.df$date[which(wy.df$wyday==sel.day)]
```
```{r}
baseflow.df <- data.frame(
  FB = (wy.df$FB_QP[which(wy.df$wyday<(sel.day))])*3.6/site.areas[1],
  TG = (wy.df$TG_QP[which(wy.df$wyday<(sel.day))])/site.areas[2]*3.6,
  BC = (wy.df$BC_QP[which(wy.df$wyday<(sel.day))])/site.areas[3]*3.6,
  TF = (wy.df$TF_QP[which(wy.df$wyday<(sel.day))])/site.areas[4]*3.6,
  RH = (wy.df$RH_QP[which(wy.df$wyday<(sel.day))])/site.areas[5]*3.6,
  RS = NA,
  TS = (wy.df$TS_QP[which(wy.df$wyday<(sel.day))])/site.areas[7]*3.6,
  SC = (wy.df$SC_QP[which(wy.df$wyday<(sel.day))])/site.areas[8]*3.6,
  WC = (wy.df$WC_QP[which(wy.df$wyday<(sel.day))])/site.areas[9]*3.6,
  GC = (wy.df$GC_QP[which(wy.df$wyday<(sel.day))])/site.areas[10]*3.6,
  WS = NA,
  FD = (wy.df$FD_QP[which(wy.df$wyday<(sel.day))])/site.areas[12]*3.6,
  date = wy.df$date[which(wy.df$wyday<(sel.day))]
)
```

```{r}
choices <- c(1,2,3,4,5,12)
site.choices <- siteabbr[choices]

plot.cols <- which(substr(colnames(wy.df),1,2) %in% site.choices)

na.check = rep(NA,length(plot.cols))
for(i in 1:length(plot.cols)){
  na.check[i] <- sum(is.na(wy.df[,plot.cols[i]]))
}

data.frame('sites'=site.choices,'ID' = choices, 'column' = plot.cols, 'NA_count' = na.check)

```
```{r}
boxplot(baseflow.df[,choices], 
        xlab = 'catchment', col = linecols[choices], ylab = 'discharge (mm/hr)', 
        ylim = c(0,0.06),
        main = paste('Normalized baseflows', water.year))
axis(side=1, at = 1:length(choices), labels = siteabbr[choices])
```


```{r}
apply(baseflow.df[,choices],2,FUN = median, na.rm = T)
```
```{r}
apply(baseflow.df[,choices],2,FUN = IQR, na.rm = T)

```






--- Conductance plots
```{r}
choices <- c(6,7,8,9)
choices <- c(1,3,4,5,9)
site.choices <- siteabbr[choices]

plot.cols <- which(substr(colnames(wy.df),1,2) %in% site.choices)

na.check = rep(NA,length(plot.cols))
for(i in 1:length(plot.cols)){
  na.check[i] <- sum(is.na(wy.df[,plot.cols[i]]))
}

data.frame('sites'=site.choices,'ID' = choices, 'column' = plot.cols, 'NA_count' = na.check)

```


```{r}
a <- 120
b <- 320

par(mar = c(4,4,5,6))
plot(wy.df$FB_QP, xaxt = 'n', xlab = 'day', ylab = 'normalized Q (mm/hr)',
     xlim = c(a,b),ylim = c(100,500),
     main = paste('discharge for Logan subcatchments -', water.year),type = 'n')
axis(1, at = seq(a,b, length.out = 8), labels = (wy.df$day[seq(a,b,length.out = 8)]))

for (i in 1:length(plot.cols)){
  lines(wy.df[,plot.cols[i]], col = linecols[choices[i]], lty = linetypes[choices[i]])
}

#lines(wy.df$FB_QP*3.6/site.areas[1], col = linecols[1])




legend('right', inset = -0.2, legend = site.choices, lty = linetypes[choices], col = linecols[choices], xpd = T)
```
