---
title: "LRO Aggregate"
author: "Daniel Thurber"
date: "2/22/2021"
output: pdf_document
---

Input the name of the file within the designated folder and read the csv into a dataframe.
```{r}
library(naniar)
library(ggplot2)
mypath <- 'C:/Users/Daniel/Documents/Research/data/new_LRO_aquatic/' #leave this directory alone!
sitecodes <- c('LR_FB_BA', 'LR_TG_BA', 'BC_CONF_A', 'TF_CONF_A','RHF_CONF_A','RS_CONF_A',
                'TF_SAWM_A', 'SPC_CONF_A', 'LR_WC_A', 'LR_GCB_A', 'WCS_CONF_A', 'LR_FD')
sitenames <- c('Franklin Basin', 'Tony Grove', 'Beaver Creek', 'Temple Fork', 'Right Hand Fork','Ricks Spring', 
               'TF at Sawmill', 'Spawn Creek', 'Above Wood Camp', 'Guinavah Campground','Wood Camp Spring', 'First Dam')
i <-11

site <- sitecodes[i]               #enter site code for file upload and export
sitename <- sitenames[i]        #enter site name for plotting
paste('Site:', sitecodes[i], '-', sitenames[i])
maxT <- 100 #initially set these values high
maxC <- 1500 #they can be honed in later in the script
```

Open all files and save as dataframes.
```{r}

qfile <- paste0(site,'_Q.csv')
qdf <- read.csv(paste0(mypath,qfile), stringsAsFactors = F)
tfile <-  paste0(site,'_T.csv')
tdf <- read.csv(paste0(mypath,tfile), stringsAsFactors = F)
cfile <-  paste0(site,'_SC.csv')
cdf <- read.csv(paste0(mypath,cfile), stringsAsFactors = F)
```


Find the first date where data was collected.
```{r}
qstart <- as.Date(qdf$DateTime[1], '%m / %d / %Y %H:%M')
qstart
cstart <- as.Date(cdf$DateTime[1], '%m / %d / %Y %H:%M')
cstart
tstart <- as.Date(tdf$DateTime[1], '%m / %d / %Y %H:%M')
tstart
mindate <- min(qstart,cstart,tstart)
paste('Start of record:', mindate)

qend <- as.Date(qdf$DateTime[nrow(qdf)], '%m / %d / %Y %H:%M')
cend <- as.Date(cdf$DateTime[nrow(cdf)], '%m / %d / %Y %H:%M')
tend <- as.Date(tdf$DateTime[nrow(tdf)], '%m / %d / %Y %H:%M')
maxdate <- max(qend,cend, tend)
maxdate <- as.Date(maxdate, '%m / %d / %Y')
paste('End of record:', maxdate)
```
Plot each series as is
```{r}
plot(qdf$Value, type = 'l', main = 'discharge', ylab = 'discharge', ylim = c(0, max(qdf$Value, na.rm = T)))
plot(cdf$Value, type = 'l', main = 'conductance', ylab = 'conductance', ylim = c(0, max(cdf$Value, na.rm = T)))
plot(tdf$Value, type = 'l', main = paste('temp at', sitename), ylab = 'temp', ylim = c(0, max(tdf$Value, na.rm = T)))
```



Add column for date and discharge/conductance/temperature, replace all low values with NA
USER: check for reasonable threshold levels.  They should be rather extreme/impossible
```{r}
minQ <- 0.00001                     #below these thresholds, values will be replaced with NA
minT <- -1
minC <- 10
maxQ <- 1000
maxT <- 200
maxC <- 8000

qdf$date <- as.Date(qdf$DateTime, '%m / %d / %Y %H:%M')
qdf$discharge <- (as.numeric(qdf$Value))
qdf$discharge <- replace(qdf$discharge, qdf$discharge<minQ, NA)
qdf$discharge <- replace(qdf$discharge, qdf$discharge>maxQ, NA)



cdf$date <- as.Date(cdf$DateTime, '%m / %d / %Y %H:%M')
cdf$conductance <- (as.numeric(cdf$Value))
cdf$conductance <- replace(cdf$conductance, cdf$conductance<minC |cdf$conductance>maxC, NA)


tdf$date <- as.Date(tdf$DateTime, '%m / %d / %Y %H:%M')
tdf$temperature <- (as.numeric(tdf$Value))
tdf$temperature <- replace(tdf$temperature, tdf$temperature<minT | tdf$temperature>maxT, NA)


#qdf$WY = ifelse(qdf$month>=10, qdf$Year+1, qdf$Year) #determine water year
```

Plot each time series to see if any extreme values need to be addressed.  Set min/max
```{r}
plot(qdf$discharge, type = "l", xlab = 'Date', ylab = 'Discharge')
plot(cdf$conductance~cdf$date, type = "l", xlab = "Date", ylab = "Specific Conductance")
plot(tdf$temperature~tdf$date, type = "l", xlab = 'Date', ylab = 'Temperature')
```
--- next chunks can replace or remove remaining spikes if desired
zoom in on a specific time window - conductance
```{r}
a <- 70000     #window starting index from plot above
c <- 15000  #window length (15-min intervals)
b <- a+c

plot(cdf$conductance[a:b], type = "l", xlab = 'Date', 
     ylab = 'Conductance', xaxt='n', main = paste('Conductance at', site))
axis(1, at = seq(1,c, length.out = 6), labels = (qdf$date[seq(a,b,length.out = 6)]))

plot(cdf$conductance, type = "l", xlim = c(a,b), ylim = c(min(cdf$conductance[a:b], na.rm= T),max(cdf$conductance[a:b], na.rm=T)),
     ylab = 'Conductance', main = paste('Conductance at', site))
```


replace an individual conductance value with the previous value
```{r}
#spike.ind <- 
#cdf$conductance[spike.ind]
#cdf$conductance[spike.ind] <- cdf$conductance[spike.ind-1]
#cdf$conductance[spike.ind]

```

zoom in on a specific time window - discharge
```{r}
a <- 98000     #window starting index from plot above
c <- 1000  #window length (15-min intervals)
b <- a+c
plot(qdf$discharge[a:b], type = "l", xlab = 'Date', 
     ylab = 'Discharge', xaxt='n', main = paste('Discharge at', site))
axis(1, at = seq(1,c, length.out = 6), labels = (qdf$date[seq(a,b,length.out = 6)]))

plot(qdf$discharge, type = "l", xlim = c(a,b), ylim = c(min(qdf$discharge[a:b], na.rm = T),max(qdf$discharge[a:b], na.rm = T)),
     ylab = 'Discharge', main = paste('Discharge at', site))
```

---
Calculate daily mean for each variable.  NA values are ignored.
```{r}
dailyq <- aggregate(discharge~date, qdf, FUN = "mean", na.rm = T)

dailyt <- aggregate(temperature~date, tdf, FUN = "mean", na.rm = T)

dailyc <- aggregate(conductance~date, cdf, FUN = "mean", na.rm = T)

```


Plot all three variables again
```{r}
plot(dailyq$discharge~dailyq$date, type = "l", xlab = 'Date', ylab = 'Discharge')
plot(dailyc$conductance~dailyc$date, type = "l", xlab = "Date", ylab = "Specific Conductance")
plot(dailyt$temperature~dailyt$date, type = "l", xlab = 'Date', ylab = 'Temperature')
```


merge dataframes for all overlapping values



create one dataframe with all three variables.  Plot the discharge time series, which should look identical to that plotted above, except with gaps for periods of missing data.
```{r}
qtcdf <- data.frame(date = seq(mindate, maxdate, by = 'day'))
#a row is created for each day in the period of record
qtcdf <-  merge(qtcdf, dailyq, by = 'date', all = T)
qtcdf <-  merge(qtcdf, dailyc, by = 'date', all = T)
qtcdf <-  merge(qtcdf, dailyt, by = 'date', all = T)
plot(qtcdf$discharge~qtcdf$date, type = "l", xlab = 'Date', ylab = 'Discharge', main = sitename)
plot(qtcdf$conductance~qtcdf$date, type = "l", xlab = 'Date', ylab = 'Conductance', main = sitename)
plot(qtcdf$temperature~qtcdf$date, type = "l", xlab = 'Date', ylab = 'Temperature', main = sitename)

```


```{r}
nrow(qtcdf)
nrow(dailyq)
nrow(dailyt)
nrow(dailyc)
qtcdf[which(is.na(qtcdf$conductance)),]
tail(qtcdf)
```



Add a water year column to the dataframe
```{r}
qtcdf$WY = ifelse(as.numeric(format(qtcdf$date,'%m'))>=10, 
                     as.numeric(format(qtcdf$date,'%Y'))+1, 
                     as.numeric(format(qtcdf$date,'%Y'))) #determine water year
```

```{r}
qtcdf$day <- format(as.Date(qtcdf$date),'%m-%d')
qtcdf$wyday <- 0
wydates <- data.frame(wyday = seq(1,366),
day=format(seq.Date(as.Date('2019-10-1','%Y-%m-%d'),as.Date('2020-09-30','%Y-%m-%d'),1),'%m-%d'))
head(qtcdf,3)
```


Populate water year day column with appropriate values 1-366
```{r}
for (i in 1:nrow(qtcdf)){
  qtcdf$wyday[i] <- wydates$wyday[which(wydates$day==qtcdf$day[i])]
}
head(qtcdf,3)
```


Plot all time series and look for any issues worth addressing
```{r}
day1 <- 1
#day1 <- 600 #use these values to zoom in on a specific date range
dayend <- nrow(qtcdf)
#dayend <- 680  #comment them out to return to full period of record
plot(qtcdf$date[day1:dayend],qtcdf$discharge[day1:dayend], type = 'l', col = 'cadetblue4',
     xlab = "date", ylab = "discharge (CMS)", main = paste("discharge at ", sitename))

plot(qtcdf$date[day1:dayend],qtcdf$temperature[day1:dayend], type = 'l', col = 'cadetblue4',
     xlab = "date", ylab = "temperature (C)", main = paste("temperature at ", sitename))

plot(qtcdf$date[day1:dayend],qtcdf$conductance[day1:dayend], type = 'l', col = 'cadetblue4',
     xlab = "date", ylab = "conductance ", main = paste("conductance at ", sitename))

```


double check the destination for the daily data, then save this dataframe
```{r}
write.csv(qtcdf, paste0('C:/Users/Daniel/Documents/Research/data/new_LRO_aquatic/',site,'.csv'), row.names = F)
```





