---
title: "LRO Time Series"
author: "Daniel Thurber"
date: "1/18/2021"
output: pdf_document
---

```{r}
mypath <- 'C:/Users/Daniel/Documents/Research/data/dataframes/'  #leave this as directory
library(ggplot2)
library(naniar)
sitecodes <- c('LR_FB_BA', 'LR_TG_BA', 'BC_CONF_A', 'TF_CONF_A', 'RHF_CONF_A', 
               'RS_CONF_A')
sitenames <- c('Franklin Basin', 'Tony Grove', 'Beaver Creek', 'Temple Fork', 'Right Hand Fork', 
               'Ricks Spring')
i <- 1
site <- sitecodes[i]               #enter site code for file upload and export
sitename <- sitenames[i]        #enter site name for plotting
paste('Site:', sitecodes[i], '-', sitenames[i])
   #the line color vector is used by other plotting scripts as well.  Attempt to keep it consistent
linecols <- c('brown3', 'goldenrod', 'forestgreen', 'bisque4', 'slateblue', 'sienna3', 'aquamarine3', 'magenta4')
```

Read the given csv into a dataframe.
```{r}
qtc <- read.csv(paste0(mypath,site,'.csv'), stringsAsFactors = F)
```


format date as a date and generate day column without year, then check the data formats. 
```{r}

qtc$date <- as.Date(qtc$date,'%Y-%m-%d')
qtc$day <- format(as.Date(qtc$date),'%m-%d')
qtc$wyday <- 0
head(qtc,3)
```

create a reference dataframe relating water year days to month-day format
```{r}
wydates <- data.frame(wyday = seq(1,366),
day=format(seq.Date(as.Date('2019-10-1','%Y-%m-%d'),as.Date('2020-09-30','%Y-%m-%d'),1),'%m-%d'))
```


Populate water year day column with appropriate values 1-366
```{r}
for (i in 1:nrow(qtc)){
  qtc$wyday[i] <- wydates$wyday[which(wydates$day==qtc$day[i])]
}
```

Set viewing parameters and generate a discharge plot

```{r}
xrange <- c(1,366)   #range of water year days to consider
dayticks <- 11 #number of tick marks on x axis
yrange <- c(min(qtc$discharge, na.rm = T), max(qtc$discharge, na.rm = T))
#yrange <- c(0,10)  #un-comment to set custom y-axis
pltyears <- seq(min(qtc$WY),max(qtc$WY))
#pltyears <- c(2015,2017,2019)  #un-comment to select custom year range

wylabels <- wydates$day[seq(xrange[1],xrange[2],length.out = dayticks)]
plot(qtc$wyday[which(qtc$WY==pltyears[1])],qtc$discharge[which(qtc$WY==pltyears[1])], type = 'l', 
     xlim = xrange, ylim = yrange, xaxt = 'n',
     xlab = 'Day of Year', ylab = 'Discharge (cms)', col = linecols[1],
     main = paste('Discharge of ', sitename, ' by water year'))
axis(1, at = seq(xrange[1],xrange[2],length.out = dayticks), labels = wylabels)
for (i in 2:length(pltyears)){
  lines(qtc$wyday[which(qtc$WY==pltyears[i])],qtc$discharge[which(qtc$WY==pltyears[i])],col = linecols[i])
}
legend('topleft', legend = pltyears, lty = 1, col = linecols)
```

Set viewing parameters and generate a temperature plot

```{r}
xrange <- c(1,366)   #range of water year days to consider, 1 to 366
dayticks <- 8 #number of tick marks on x axis
yrange <- c(min(qtc$temperature, na.rm = T), max(qtc$temperature, na.rm = T))
#yrange <- c(0,10)  #un-comment to set custom y-axis
pltyears <- seq(min(qtc$WY),max(qtc$WY))
#pltyears <- c(2015,2019)  #un-comment to select custom year range

wylabels <- wydates$day[seq(xrange[1],xrange[2],length.out = dayticks)]
plot(qtc$wyday[which(qtc$WY==pltyears[1])],qtc$temperature[which(qtc$WY==pltyears[1])], type = 'l', 
     xlim = xrange, ylim = yrange, xaxt = 'n',
     xlab = 'Day of Year', ylab = 'Temperature (deg C)', col = linecols[1],
     main = paste('Temperature of ', sitename, ' by water year'))
axis(1, at = seq(xrange[1],xrange[2],length.out = dayticks), labels = wylabels)
for (i in 2:length(pltyears)){
  lines(qtc$wyday[which(qtc$WY==pltyears[i])],qtc$temperature[which(qtc$WY==pltyears[i])],col = linecols[i])
}
legend('topleft', legend = pltyears, lty = 1, col = linecols)
```


Set viewing parameters and generate a specific conductance plot

```{r}
xrange <- c(1,366)   #range of water year days to consider
dayticks <- 11 #number of tick marks on x axis
yrange <- c(min(qtc$conductance, na.rm = T), max(qtc$conductance, na.rm = T))
#yrange <- c(0,10)  #un-comment to set custom y-axis
pltyears <- seq(min(qtc$WY),max(qtc$WY))
#pltyears <- c(2015,2018)  #un-comment to select custom year range

wylabels <- wydates$day[seq(xrange[1],xrange[2],length.out = dayticks)]
plot(qtc$wyday[which(qtc$WY==pltyears[1])],qtc$conductance[which(qtc$WY==pltyears[1])], type = 'l', 
     xlim = xrange, ylim = yrange, xaxt = 'n',
     xlab = 'Day of Year', ylab = 'conductance (uS/cm)', col = linecols[1],
     main = paste('Specific conductance of ', sitename, ' by water year'))
axis(1, at = seq(xrange[1],xrange[2],length.out = dayticks), labels = wylabels)
for (i in 2:length(pltyears)){
  lines(qtc$wyday[which(qtc$WY==pltyears[i])],qtc$conductance[which(qtc$WY==pltyears[i])],col = linecols[i])
}
legend('bottomleft', legend = pltyears, lty = 1, col = linecols)
```

Define a water year and plot temp and conductivity together
```{r}
pltyear <- 2019
xrange <- c(150,300)   #range of water year days to consider
dayticks <- 11 #number of tick marks on x axis
yrange <- c(min(qtc$conductance, na.rm = T), max(qtc$conductance, na.rm = T))
yrange <- c(250,420)  #un-comment to set custom y-axis

wylabels <- wydates$day[seq(xrange[1],xrange[2],length.out = dayticks)]
plot(qtc$wyday[which(qtc$WY==pltyear)],qtc$conductance[which(qtc$WY==pltyear)], type = 'l', 
     xlim = xrange, ylim = yrange, xaxt = 'n',
     xlab = 'Day of Year', ylab = 'conductance (uS/cm)', col = linecols[1],
     main = paste('SC and Temp of ', sitename, 'for water year', pltyear))
axis(1, at = seq(xrange[1],xrange[2],length.out = dayticks), labels = wylabels)

legend('bottomleft', legend = c('conductance', 'temp'
), lty = 1, col = linecols)

par(new = T)
plot(qtc$temperature[which(qtc$WY==pltyear)], 
     xlab = '', ylab = '',
     col=linecols[2], type = 'l', axes= F)
axis(side = 4, at = pretty(range(qtc$temperature)))      # Add second axis
mtext("water temp (C)", side = 4, line = 3)
```



Define a water year and plot discharge and conductivity together
```{r}
wy <- 2020
wydf <- qtc[which(qtc$WY == wy),]
xrange <- c(1,365)   #range of water year days to consider
dayticks <- 11 #number of tick marks on x axis
yrange <- c(min(wydf$conductance, na.rm = T), max(wydf$conductance, na.rm = T))
#yrange <- c(250,420)  #un-comment to set custom y-axis
mean(qtc$discharge[which(qtc$WY == wy)], na.rm = T)
```

```{r}
wylabels <- wydates$day[seq(xrange[1],xrange[2],length.out = dayticks)]
par(mar = c(4,4,2,4.5))
plot(wydf$wyday,wydf$conductance, type = 'l', 
     xlim = xrange, ylim = yrange, xaxt = 'n',
     xlab = 'Day of Year', ylab = 'conductance (uS/cm)', col = linecols[1],
     main = paste('SC and Discharge of ', sitename, 'for water year', wy))
axis(1, at = seq(xrange[1],xrange[2],length.out = dayticks), labels = wylabels)

legend('left', legend = c('conductance', 'discharge'
), lty = 1, col = linecols)

par(new = T)
plot(wydf$discharge[xrange[1]:xrange[2]], 
     xlab = '', ylab = '',
     col=linecols[2], type = 'l', axes= F)
axis(side = 4, pretty(range(wydf$discharge, na.rm = T),5))      # Add second axis
mtext("discharge", side = 4, line = 3)
```