---
title: "Metrics"
author: "Daniel Thurber"
date: "8/10/2021"
output: pdf_document
---
initialize the session
```{r}
mypath <- 'C:/Users/Daniel/Documents/Research/data/dataframes/'  #leave this as directory
library(naniar)
library(snotelr)
library(stringr)
library(zoo, warn.conflicts = F)
library(raster, warn.conflicts = F)

windowsFonts(A = windowsFont('Times New Roman'))
dayticks <- c(93,124,153, 184,214,245,275,306,337,366) #water year days corresponding to the first of the month
ticklabs <- c('Jan 1', 'Feb 1','Mar 1','Apr 1','May 1','Jun 1','Jul 1','Aug 1','Sep 1', 'Oct 1')


sitecodes <- c('LR_FB_BA', 'LR_TG_BA', 'BC_CONF_A', 'TF_CONF_A','RHF_CONF_A', 'RS_CONF_A', 
               'TF_SAWM_A', 'SPC_CONF_A', 'LR_WC_A', 'LR_GCB_A', 'WCS_CONF_A', 'LR_FD')
sitenames <- c('Franklin Basin', 'Tony Grove', 'Beaver Creek', 'Temple Fork', 'Right Hand Fork','Ricks Spring', 
               'TF at Sawmill', 'Spawn Creek', 'Above Wood Camp', 'Guinavah Campground','Wood Camp Spring','First Dam')
siteabbr <- c('FB', 'TG', 'BC', 'TF','RH', 'RS', 
              'TS', 'SC', 'WC', 'GC', 'WS','FD')

sitesnotel <- c(1115, 1115, 1114,1013,1013, 823, 
              1013, 1098, 1113, 1113, 823,1098)
ST.el <- c(7250, 7250, 7705,7406,7406, 8474, 
           7406, 8270, 6332, 6332, 8474,8270)*0.3048

#FB_484, GCS_1114, KN_1115, TF_1013, TGL_823, TGRS_1113, UDD_1098
#GCS: 7705, KN: 7250, TF: 7406, USUDD: 8270, TGRS: 6332, TGL: 8474, FB: 8140

startyear <- c(2015,2015,2016,2016,2017,2016,
               2019,2019,2019,2019,2019,2015)
acf.sites <- c('FB_', 'TG_', 'BC_', 'TF_', 'RH_', 'RS_', 'TS_', 'SC_', 'WC_', 'GC_', 'WS_', 'FD_')
acf.years <- c('15','16','17','18','19','20','21')
plot.points <- c(1,5,7,8,15,17,19)
year.type <- c('(Normal)', '(Normal)', '(Wet)', '(Dry)', '(Wet)', '(Normal)', '(Dry)')


linecols <- c('brown3', 'goldenrod', 'forestgreen', 'bisque4', 'slateblue', 'tan1', 
              'aquamarine3', 'magenta4', 'sienna3','cyan','violetred2','yellow2')
linetypes <- c(1,1,1,1,1,3,1,1,1,1,4,1)
rgbmat <- col2rgb(linecols)
wydates <- data.frame(wyday = seq(1,366),
day=format(seq.Date(as.Date('2019-10-1','%Y-%m-%d'),as.Date('2020-09-30','%Y-%m-%d'),1),'%m-%d'))
comp.df <- read.csv(paste0('C:/Users/Daniel/Documents/Research/data/dataframes/catchment_comparison.csv'))
corr.df <- read.csv('C:/Users/Daniel/Documents/Research/data/dataframes/correlograms.csv')
colnames(comp.df)[4:ncol(comp.df)] <- str_sub(colnames(comp.df)[4:ncol(comp.df)],-6,-1) #make sure column names are only the last 6 characters
row.names(comp.df) <- sitecodes
data.frame(A=row.names(comp.df),B=comp.df[,'site_name'])==data.frame(A=sitecodes, B = sitenames)#verify that row names match up

head(comp.df[,which(colSums(comp.df[,4:ncol(comp.df)],na.rm = T)!=0)+3],3)
```
Look at values for a specific variable
```{r}
myvar <-'MMQ'
comp.df[,which(substr(colnames(comp.df),4,6)==myvar)]
```
Hard code a single value
```{r}

comp.df['WCS_CONF_A','18_QRM'] #<- NA
```


initialize site areas (km^2)
```{r}
site.areas <- c(65.9767, #FB
                277.965, #TG
                103.4015, #BC
                41.4076, #TF
                65.1986, #RH
                NA, #RS
                8.6085, #TS
                14.7168, #SC
                403.874, #WC
                520.8331, #GC
                NA, #WS
                554 #FD
                )
```

select a site to work with
```{r}
i <-7#enter site INDEX for file upload and export

site <- sitecodes[i]               
sitename <- sitenames[i]
siteabv <- siteabbr[i]
sitenum <- i
crossdf <- read.csv(paste0('C:/Users/Daniel/Documents/Research/data/dataframes/patched_data/',site,'_patched.csv'))


crossdf$date <- as.Date(crossdf$date,'%Y-%m-%d')
head(crossdf,3)
paste('Site:', site, '-',sitename)
```

### manually add a new column of values
select a site to work with
```{r}
i <-7#enter site INDEX for file upload and export

site <- sitecodes[i]               
sitename <- sitenames[i]
siteabv <- siteabbr[i]
sitenum <- i
crossdf <- read.csv(paste0('C:/Users/Daniel/Documents/Research/data/dataframes/patched_data/',site,'_patched.csv'))


crossdf$date <- as.Date(crossdf$date,'%Y-%m-%d')
head(crossdf,3)
paste('Site:', site, '-',sitename)
```
Manually create vectors of metrics/catchment attributes

```{r}
HI = c(0.473, 0.502, 0.519, 0.491, 0.564, NA, 0.566, 0.514, 0.542, 0.519, NA, NA)
KST = c(65, 50, 94, 63, 46, NA, 99, 46, 70, 69, NA, 71)
```


```{r}
new.col.name <- 'CV_KST' #define the column name as a character string
new.col.values <- KST #define all values in sequence, or reference a vector with them

comp.df[,new.col.name] <- new.col.values #add values to the dataframe
comp.df[,c(1,2,3,which(colnames(comp.df)==new.col.name))] #display the dataframe
```

```{r}
write.csv(comp.df, paste0('C:/Users/Daniel/Documents/Research/data/dataframes/catchment_comparison.csv'), row.names = F)
paste('data for',site,'saved at',date())
```



### Extract and compile FFC metrics
select a site to work with
```{r}
i <-7#enter site INDEX for file upload and export

site <- sitecodes[i]               
sitename <- sitenames[i]
siteabv <- siteabbr[i]
sitenum <- i
crossdf <- read.csv(paste0('C:/Users/Daniel/Documents/Research/data/dataframes/patched_data/',site,'_patched.csv'))


crossdf$date <- as.Date(crossdf$date,'%Y-%m-%d')
head(crossdf,3)
paste('Site:', site, '-',sitename)
```

---Read metrics from functional flow calculator for specific site
```{r}
FFCmets <- read.csv(paste0('C:/Users/Daniel/Documents/Research/data/dataframes/FFC_data/',siteabv,'_metrics.csv'))
rownames(FFCmets) = FFCmets[,1]
colnames(FFCmets)[1] <- 'var'
FFCmets
```

Filter to only the desired magnitude and timing metrics
```{r}
colnames(FFCmets)[2:ncol(FFCmets)] <- str_sub(colnames(FFCmets)[2:ncol(FFCmets)],-2,-1)
FFCtims <- FFCmets[c('Wet_Tim_Water', 'SP_Tim','DS_Tim'),-1]
FFCmets <- FFCmets[c('DS_Mag_50','SP_ROC'),-1]
FFCmets
FFCtims
```
remove columns with all NA values
```{r}
FFCmets <- FFCmets[,-which((colSums(FFCmets, na.rm = T)==0))]#FFCmets[,-which(is.na(colSums(FFCmets)))]  
FFCmets
```

transfer all MAGNITUDE metrics into comp.df
```{r}
all.mets <- c()
for (y in 1:ncol(FFCmets)) {
  mets <- paste0(colnames(FFCmets)[y],c('_BFM','_RRC'))
  vals <- FFCmets[,y]

  for (i in 1:length(mets)){
    comp.df[site,mets[i]] <- vals[i]
  }


  all.mets <- c(all.mets,mets)
  }
comp.df[site,all.mets]
```


Remove columns with all NA values
```{r}
FFCtims <- FFCtims[,-which((colSums(FFCtims, na.rm = T)==0))]

FFCtims

```

transfer all TIMING values into comp.df
```{r}
all.tims <- c()
for (y in 1:ncol(FFCtims)) {
  tims <- paste0(colnames(FFCtims)[y],c('_MSD', '_RSD','_BSD'))
  vals <- FFCtims[,y]

  for (i in 1:length(tims)){
    comp.df[site,tims[i]] <- vals[i]
  }


  all.tims <- c(all.tims,tims)
  }
comp.df[site,all.tims]
```
---select a water year and plot discharge with timing metrics
```{r}
wateryear <- 2021
wydf <- crossdf[which(crossdf$WY==wateryear),]
year.char <- as.character(wateryear-2000)

par(mar = c(4,4,4,6))
a <- 150 #index to start plot
b <- 350 #end of viewing window
#barplot(wydf$SWI[a:b], axes = F, type = 'n')


#par(new=T)
par(family = 'A')
yrange = range(wydf$qpatch[a:b], na.rm = T)
#plot discharge over the window.  The line gets plotted later over the highlight rectangles
plot(wydf$qpatch, xlim = c(a, b), ylim = yrange, type = 'l', ylab = 'Discharge (m^3/s)', 
     col = linecols[i],
     main = paste('Discharge at', sitename,wydf$WY[a]), xaxt = 'n', xlab = 'date'
     )
#axis(side = 4, at = pretty(range(wydf$SWI[a:b]), n = 4),main = 'SWI')
#mtext('Surface water input (mm)', side = 4, line = 2)

axis(1, at = dayticks, labels = ticklabs)

timcolor <- c('green', 'orange','blue')

abline(v = which(wydf$wyday==comp.df[site,paste0(year.char,'_MSD')]), col = timcolor[1])
abline(v = which(wydf$wyday==comp.df[site,paste0(year.char,'_RSD')]), col = timcolor[2])
abline(v = which(wydf$wyday==comp.df[site,paste0(year.char,'_BSD')]), col = timcolor[3])

legend('topright', lty = 1, col = c(linecols[i],timcolor[1:2]), legend = c('discharge','melt start', 'recession start'))
```

Manually set timing values, then check on a plot
```{r}
rep.met <- 'RSD' #MSD, RSD, or BSD
val <- 245#enter water year day to try: MSD~150, RSD~250, BSD <- 365 

yr <- paste0(as.character(wateryear-2000),'_')
comp.df[site,paste0(yr,rep.met)] <- val

plot(wydf$qpatch, xlim = c(which(wydf$wyday==val)-40, which(wydf$wyday==val)+40), ylim = yrange, type = 'l', ylab = 'Discharge (m^3/s)', 
     col = linecols[i],
     main = paste('SWI & discharge at', sitename,wydf$WY[a]), xlab = 'date'
     )

abline(v = which(wydf$wyday==comp.df[site,paste0(year.char,'_MSD')]), col = timcolor[1])
abline(v = which(wydf$wyday==comp.df[site,paste0(year.char,'_RSD')]), col = timcolor[2])
abline(v = which(wydf$wyday==comp.df[site,paste0(year.char,'_BSD')]), col = timcolor[3])
```



save updated catchment_comparison file (comp.df)
```{r}
write.csv(comp.df, paste0('C:/Users/Daniel/Documents/Research/data/dataframes/catchment_comparison.csv'), row.names = F)
paste('data for',sitename,'saved to catchment_comparison.csv at',date())
```
### Catchment Variables
---Hypsometric integral (HYI) & Snotel elevation exceedance
```{r}
for (num in which(!is.na(site.areas))) {
site <- sitecodes[num]               
sitename <- sitenames[num]
siteabv <- siteabbr[num]
sitenum <- num
rast.dir <- 'C:/Users/Daniel/Documents/Research/hypsometric_curves/'
Eraster <- paste0(siteabv, '_DEM.tif')
DEM <- raster(paste0(rast.dir,Eraster))
elevFreq <- freq(DEM)


truelev <- data.frame(elevFreq[c(1:(nrow(elevFreq)-1)),]) #ignores last row with NA values
#truelev <- data.frame(elevFreq[-c(1,2),]) #use this to remove any rows
for (i in seq(1,nrow(truelev))){
  truelev$sum[i] <- sum(truelev$count[1:i])
}

truelev$CDVal <- truelev$sum/sum(truelev$count)
minelev <- min(truelev$value)
maxelev <- max(truelev$value)
elevrange <- maxelev - minelev+1
truelev$elevprop <- (truelev$value-minelev)/elevrange
HYI <- 1-sum(truelev$CDVal)/(elevrange)
SEE <- 1-truelev$CDVal[which(truelev$value==round(ST.el[num]))]
comp.df[site,'CV_HYI'] <- HYI
comp.df[site,'CV_SEE'] <- SEE
}
```

---median slope (MDS)
```{r}
for (num in which(!is.na(site.areas))) {
site <- sitecodes[num]               
sitename <- sitenames[num]
siteabv <- siteabbr[num]
sitenum <- num
rast.dir <- 'C:/Users/Daniel/Documents/Research/hypsometric_curves/'
Sraster <- paste0('S_',siteabv,'.tif')
Slope <- raster(paste0(rast.dir,Sraster))
MDS <- quantile(Slope,.5)
comp.df[site,'CV_MDS'] <- MDS
}
```

---Median elevation (MDE)
```{r}
for (num in which(!is.na(site.areas))) {

site <- sitecodes[num]               
sitename <- sitenames[num]
siteabv <- siteabbr[num]
sitenum <- num
rast.dir <- 'C:/Users/Daniel/Documents/Research/hypsometric_curves/'
Eraster <- paste0(siteabv, '_DEM.tif')

DEM <- raster(paste0(rast.dir,Eraster))

MDE <- quantile(DEM, .5)
comp.df[site,'CV_MDE'] <- MDE
}
```

---Vector-averaged aspect (VAA)
```{r}
for (num in which(!is.na(site.areas))) {
site <- sitecodes[num]               
sitename <- sitenames[num]
siteabv <- siteabbr[num]
sitenum <- num
rast.dir <- 'C:/Users/Daniel/Documents/Research/hypsometric_curves/'
Araster <- paste0('A_',siteabv, '.tif')

aspect <- raster(paste0(rast.dir,Araster))

a.df <- na.omit(as.data.frame(aspect))
a.df[(which(a.df[,1]==-1)),1] <- NA  #replace level pixels (A = -1) with NA
a.df$sin <- sin(a.df[,1]*pi/180)
a.df$cos <- cos(a.df[,1]*pi/180)

sinMean <- mean(a.df$sin, na.rm = T)
cosMean <- mean(a.df$cos, na.rm = T)
aspMean <- atan(sinMean/cosMean)/pi*180
if(sinMean<0 & cosMean>0){
  aspMean <- aspMean+360}
if(cosMean<0){
  aspMean <- aspMean+180
}
VAA <- aspMean
comp.df[site,'CV_VAA'] <- VAA
}
```

---Median Hillshade (MHS)
```{r}
for (num in which(!is.na(site.areas))) {

site <- sitecodes[num]               
sitename <- sitenames[num]
siteabv <- siteabbr[num]
sitenum <- num
rast.dir <- 'C:/Users/Daniel/Documents/Research/hypsometric_curves/'
Hraster <- paste0('H_',siteabv, '.tif')

HillShade <- raster(paste0(rast.dir,Hraster))

MHS <- quantile(HillShade, .5)
comp.df[site,'CV_MHS'] <- MHS
}
```

---Save to .csv
```{r}
write.csv(comp.df, paste0('C:/Users/Daniel/Documents/Research/data/dataframes/catchment_comparison.csv'), row.names = F)
paste('data for',sitename,'saved to catchment_comparison.csv at',date())
```

### Baseflow Metrics
--- calculate median baseflow ('BFM')
```{r}
for (num in 1:12){
  site <- sitecodes[num]               
sitename <- sitenames[num]
siteabv <- siteabbr[num]
sitenum <- num
crossdf <- read.csv(paste0('C:/Users/Daniel/Documents/Research/data/dataframes/patched_data/',site,'_patched.csv'))


crossdf$date <- as.Date(crossdf$date,'%Y-%m-%d')

for (ii in startyear[num]:2021){

wateryear <- ii
wydf <- crossdf[which(crossdf$WY==wateryear),]
year.char <- as.character(wateryear-2000)


bsd <- comp.df[site,paste0(year.char,'_BSD')]
msd <- comp.df[site,paste0(year.char,'_MSD')]

which(wydf$wyday >= bsd & wydf$wyday < msd)
bflows <- wydf[c(bsd:msd),'qpatch']

bfm <- median(bflows, na.rm = T)

comp.df[site,paste0(year.char,'_BFM')] <- bfm
}}
paste("BFM Calculated for", sitename)
```

--- Minimum 7-day average ('QRM')
```{r}
for (num in 1:12){
  site <- sitecodes[num]               
sitename <- sitenames[num]
siteabv <- siteabbr[num]
sitenum <- num
crossdf <- read.csv(paste0('C:/Users/Daniel/Documents/Research/data/dataframes/patched_data/',site,'_patched.csv'))


crossdf$date <- as.Date(crossdf$date,'%Y-%m-%d')

for (ii in startyear[num]:2021){
  
wateryear <- ii
wydf <- crossdf[which(crossdf$WY==wateryear),]
year.char <- as.character(wateryear-2000)

minroll <- min(rollmean(wydf$qpatch,7), na.rm = T)
comp.df[site,paste0(year.char,'_QRM')] <- minroll
}}

paste("QRM Calculated for", sitename)
```

--- Winter Flow Index ('WFI')
```{r}

for (num in 1:12){
  site <- sitecodes[num]               
sitename <- sitenames[num]
siteabv <- siteabbr[num]
sitenum <- num
crossdf <- read.csv(paste0('C:/Users/Daniel/Documents/Research/data/dataframes/patched_data/',site,'_patched.csv'))


crossdf$date <- as.Date(crossdf$date,'%Y-%m-%d')

for (ii in startyear[num]:2021){
  
wateryear <- ii
wydf <- crossdf[which(crossdf$WY==wateryear),]
year.char <- as.character(wateryear-2000)

QRM <- min(rollmean(wydf$qpatch,7), na.rm = T)
WFI <- QRM/mean(wydf$qpatch)
comp.df[site,paste0(year.char,'_WFI')] <- WFI
}}

paste("WFI Calculated for", sitename)
```

--- Days of Q|SWIT correlation (BQS)
```{r}

for (num in c(1:5,12)){
  site <- sitecodes[num]               
sitename <- sitenames[num]
siteabv <- siteabbr[num]
sitenum <- num
crossdf <- read.csv(paste0('C:/Users/Daniel/Documents/Research/data/dataframes/',site,'_mod.csv'))

crossdf$date <- as.Date(crossdf$date,'%Y-%m-%d')

for (ii in startyear[num]:2018){
lagmax <- 60
wateryear <- ii
wydf <- crossdf[which(crossdf$WY==wateryear),]
year.char <- as.character(wateryear-2000)

bsd <- comp.df[site,paste0(year.char,'_BSD')]
msd <- comp.df[site,paste0(year.char,'_MSD')]

bflows <- wydf[which(wydf$wyday >= bsd & wydf$wyday < msd),]


bccf <- ccf(bflows$qpatch, bflows$SWIT, lag.max = lagmax, 
             plot = F, na.action = na.pass)

lagmax <- max(bccf$lag)

BQS <- sum(bccf$acf[(lagmax+1):(2*lagmax+1)]>=0.2)

comp.df[site,paste0(year.char,'_BQS')] <- BQS
}}
paste("BQS Calculated for", sitename)

```

--- Save the dataframe
```{r}
write.csv(comp.df, paste0('C:/Users/Daniel/Documents/Research/data/dataframes/catchment_comparison.csv'), row.names = F)
paste('data for',sitename,'saved to catchment_comparison.csv at',date())
```

### Melt Metrics
--- Melt season runoff ratio (MRR)
```{r}
#num <- 1
for (num in c(1:5,12)){
  site <- sitecodes[num]               
sitename <- sitenames[num]
siteabv <- siteabbr[num]
sitenum <- num
crossdf <- read.csv(paste0('C:/Users/Daniel/Documents/Research/data/dataframes/',site,'_mod.csv'))

crossdf$date <- as.Date(crossdf$date,'%Y-%m-%d')

for (ii in startyear[num]:2018){

wateryear <- ii
wydf <- crossdf[which(crossdf$WY==wateryear),]
year.char <- as.character(wateryear-2000)

    msd <- comp.df[site,paste0(year.char,'_MSD')]
    rsd <- comp.df[site,paste0(year.char,'_RSD')]+30

     mflows <- wydf[which(wydf$wyday >= msd & wydf$wyday < rsd),]
    
totalQ <- sum(mflows$qpatch)/site.areas[num]*3.6*24
totalSWIT <- sum(mflows$SWIT)*1000



mrr <- totalQ/totalSWIT

comp.df[site,paste0(year.char,'_MRR')] <- mrr
}}
paste("MRR Calculated for", sitename)
``` 

--- Q|SWIT lag to peak of correlation (QMP)
```{r}

for (num in c(1:5,12)){
  site <- sitecodes[num]               
sitename <- sitenames[num]
siteabv <- siteabbr[num]
sitenum <- num
crossdf <- read.csv(paste0('C:/Users/Daniel/Documents/Research/data/dataframes/',site,'_mod.csv'))

crossdf$date <- as.Date(crossdf$date,'%Y-%m-%d')

for (ii in startyear[num]:2018){
lagmax <- 60
wateryear <- ii
wydf <- crossdf[which(crossdf$WY==wateryear),]
year.char <- as.character(wateryear-2000)

msd <- comp.df[site,paste0(year.char,'_MSD')]-30
rsd <- comp.df[site,paste0(year.char,'_RSD')]

mflows <- wydf[which(wydf$wyday >= msd & wydf$wyday < rsd),]


mccf <- ccf(mflows$qpatch, mflows$SWIT, lag.max = lagmax, 
             plot = F, na.action = na.pass)

lagmax <- max(mccf$lag)

QMP <- mccf$lag[which(mccf$acf==max(mccf$acf[(lagmax+1):(2*lagmax+1)]))]

comp.df[site,paste0(year.char,'_QMP')] <- QMP
}}
paste("QMP Calculated for", sitename)

```

--- Q|SWIT end of correlation (QMC)
```{r}
for (num in 1:5){
  site <- sitecodes[num]               
  sitename <- sitenames[num]
  siteabv <- siteabbr[num]
  sitenum <- num
  crossdf <- read.csv(paste0('C:/Users/Daniel/Documents/Research/data/dataframes/',site,'_mod.csv'))
  
  crossdf$date <- as.Date(crossdf$date,'%Y-%m-%d')
  
  for (ii in startyear[num]:2018){
    lagmax <- 60
    wateryear <- ii
    wydf <- crossdf[which(crossdf$WY==wateryear),]
    year.char <- as.character(wateryear-2000)
    
    msd <- comp.df[site,paste0(year.char,'_MSD')]-30
    rsd <- comp.df[site,paste0(year.char,'_RSD')]
    
    mflows <- wydf[which(wydf$wyday >= msd & wydf$wyday < rsd),]
    
    
    mccf <- ccf(mflows$qpatch, mflows$SWIT, lag.max = lagmax, 
                 plot = F, na.action = na.pass)
    lagmax <- max(mccf$lag)
    
    QMC <- which(abs(mccf$acf)[(lagmax+1):(2*lagmax+1)]<0.2)[1]-1
    
    comp.df[site,paste0(year.char,'_QMC')] <- QMC
}}
paste("QMC Calculated for", sitename)

```

--- Discharge ACF end of correlation (MQA)
```{r}
for (num in 1:12){
  site <- sitecodes[num]               
sitename <- sitenames[num]
siteabv <- siteabbr[num]
sitenum <- num
crossdf <- read.csv(paste0('C:/Users/Daniel/Documents/Research/data/dataframes/patched_data/',site,'_patched.csv'))

crossdf$date <- as.Date(crossdf$date,'%Y-%m-%d')

for (ii in startyear[num]:2021){
wateryear <- ii
wydf <- crossdf[which(crossdf$WY==wateryear),]
year.char <- as.character(wateryear-2000)


rsd <- comp.df[site,paste0(year.char,'_RSD')]
msd <- comp.df[site,paste0(year.char,'_MSD')]

mflows <- wydf[which(wydf$wyday >= msd & wydf$wyday < rsd),'qpatch']


macf <- acf(mflows, lag.max = 80, plot = F, na.action = na.pass)
MQA <- which(abs(macf$acf)<0.2)[1]-1

comp.df[site,paste0(year.char,'_MQA')] <- MQA
}}
paste("MQA Calculated for", sitename)

```

--- Conductance ACF end of correlation (MCA)
```{r}
for (num in 1:9){
  site <- sitecodes[num]               
sitename <- sitenames[num]
siteabv <- siteabbr[num]
sitenum <- num
crossdf <- read.csv(paste0('C:/Users/Daniel/Documents/Research/data/dataframes/patched_data/',site,'_patched.csv'))


crossdf$date <- as.Date(crossdf$date,'%Y-%m-%d')

for (ii in startyear[num]:2021){
wateryear <- ii
wydf <- crossdf[which(crossdf$WY==wateryear),]
year.char <- as.character(wateryear-2000)


rsd <- comp.df[site,paste0(year.char,'_RSD')]
msd <- comp.df[site,paste0(year.char,'_MSD')]

mcond <- wydf[which(wydf$wyday >= msd & wydf$wyday < rsd),'cpatch']


macf <- acf(mcond, lag.max = 80, plot = F, na.action = na.pass)
MCA <- which(abs(macf$acf)<0.2)[1]-1

comp.df[site,paste0(year.char,'_MCA')] <- MCA
}}
paste("MCA Calculated for", sitename)

```

--- Total melt discharge (MMQ)
```{r}
#num <- 1
for (num in 1:12){
  site <- sitecodes[num]               
sitename <- sitenames[num]
siteabv <- siteabbr[num]
sitenum <- num
crossdf <- read.csv(paste0('C:/Users/Daniel/Documents/Research/data/dataframes/patched_data/',site,'_patched.csv'))

crossdf$date <- as.Date(crossdf$date,'%Y-%m-%d')

for (ii in startyear[num]:2021){

wateryear <- ii
wydf <- crossdf[which(crossdf$WY==wateryear),]
year.char <- as.character(wateryear-2000)


rsd <- comp.df[site,paste0(year.char,'_RSD')]
msd <- comp.df[site,paste0(year.char,'_MSD')]

mflows <- wydf[c(msd:(rsd+60)),]

mmq <- sum(mflows$qpatch, na.rm = T)

comp.df[site,paste0(year.char,'_MMQ')] <- mmq}}
paste("MMQ Calculated for", sitename)
```

--- maximum daily average discharge (MXQ)
```{r}
for (num in 1:12){
  site <- sitecodes[num]               
sitename <- sitenames[num]
siteabv <- siteabbr[num]
sitenum <- num
crossdf <- read.csv(paste0('C:/Users/Daniel/Documents/Research/data/dataframes/patched_data/',site,'_patched.csv'))

crossdf$date <- as.Date(crossdf$date,'%Y-%m-%d')

for (ii in startyear[num]:2021){

wateryear <- ii
wydf <- crossdf[which(crossdf$WY==wateryear),]
year.char <- as.character(wateryear-2000)


rsd <- comp.df[site,paste0(year.char,'_RSD')]
msd <- comp.df[site,paste0(year.char,'_MSD')]

mflows <- wydf[c(msd:rsd),]

mxq <- max(mflows$qpatch, na.rm = T)

comp.df[site,paste0(year.char,'_MXQ')] <- mxq
}}
paste("MMQ Calculated for", sitename)
```

--- Save dataframe
```{r}
write.csv(comp.df, paste0('C:/Users/Daniel/Documents/Research/data/dataframes/catchment_comparison.csv'), row.names = F)
paste('data for',sitename,'saved to catchment_comparison.csv at',date())
```

### Recession Metrics
Isolate recession flows:
```{r}
wateryear <- 2020
wydf <- crossdf[which(crossdf$WY==wateryear),]
year.char <- as.character(wateryear-2000)


rsd <- comp.df[site,paste0(year.char,'_RSD')]
if (rsd<265) {
  red <- rsd+100
} else {
  red <- 365
}

which(wydf$wyday >= rsd & wydf$wyday < red)

rflows <- wydf[which(wydf$wyday >= rsd & wydf$wyday < red),'qpatch']
plot(rflows, type = 'l')
```

Discharge ACF end of correlation (RQA)
```{r}
for (num in 1:12){
  site <- sitecodes[num]               
sitename <- sitenames[num]
siteabv <- siteabbr[num]
sitenum <- num
crossdf <- read.csv(paste0('C:/Users/Daniel/Documents/Research/data/dataframes/patched_data/',site,'_patched.csv'))


crossdf$date <- as.Date(crossdf$date,'%Y-%m-%d')

for (ii in startyear[num]:2021){
wateryear <- ii
wydf <- crossdf[which(crossdf$WY==wateryear),]
year.char <- as.character(wateryear-2000)


rsd <- comp.df[site,paste0(year.char,'_RSD')]
if (rsd<265) {
  red <- rsd+100
} else {
  red <- 365
}

rflows <- wydf[which(wydf$wyday >= rsd & wydf$wyday < red),'qpatch']

racf <- acf(rflows, lag.max = 80, plot = F, na.action = na.pass)
RQA <- which(abs(racf$acf)<0.2)[1]-1

comp.df[site,paste0(year.char,'_RQA')] <- RQA
}}
paste("RQA Calculated for", sitename)

```

Conductance ACF end of correlation (RCA)
```{r}
for (num in 1:9){
  site <- sitecodes[num]               
sitename <- sitenames[num]
siteabv <- siteabbr[num]
sitenum <- num
crossdf <- read.csv(paste0('C:/Users/Daniel/Documents/Research/data/dataframes/patched_data/',site,'_patched.csv'))


crossdf$date <- as.Date(crossdf$date,'%Y-%m-%d')

for (ii in startyear[num]:2021){
wateryear <- ii
wydf <- crossdf[which(crossdf$WY==wateryear),]
year.char <- as.character(wateryear-2000)


rsd <- comp.df[site,paste0(year.char,'_RSD')]
if (rsd<265) {
  red <- rsd+100
} else {
  red <- 365
}

rcond <- wydf[which(wydf$wyday >= rsd & wydf$wyday < red),'cpatch']

racf <- acf(rcond, lag.max = 80, plot = F, na.action = na.pass)
RCA <- which(abs(racf$acf)<0.2)[1]-1

comp.df[site,paste0(year.char,'_RCA')] <- RCA
}
paste("RCA Calculated for", sitename)
}
```

Weekly recession rate of change (RRW)
```{r}
for (num in 1:12){
  site <- sitecodes[num]               
sitename <- sitenames[num]
siteabv <- siteabbr[num]
sitenum <- num
crossdf <- read.csv(paste0('C:/Users/Daniel/Documents/Research/data/dataframes/patched_data/',site,'_patched.csv'))


crossdf$date <- as.Date(crossdf$date,'%Y-%m-%d')
for (ii in startyear[num]:2021){
wateryear <- ii
wydf <- crossdf[which(crossdf$WY==wateryear),]
year.char <- as.character(wateryear-2000)


rsd <- comp.df[site,paste0(year.char,'_RSD')]
if (rsd<265) {
  red <- rsd+100
} else {
  red <- 365
}

rflows <- wydf[which(wydf$wyday >= rsd & wydf$wyday < red),'qpatch']

RRW <- (rflows[1]-rflows[8])/(7*site.areas[num])

comp.df[site,paste0(year.char,'_RRW')] <- RRW
}}
paste("RRW Calculated for", sitename)

```

Monthly recession rate of change (RRM)
```{r}
for (num in 1:12){
  site <- sitecodes[num]               
sitename <- sitenames[num]
siteabv <- siteabbr[num]
sitenum <- num
crossdf <- read.csv(paste0('C:/Users/Daniel/Documents/Research/data/dataframes/patched_data/',site,'_patched.csv'))


crossdf$date <- as.Date(crossdf$date,'%Y-%m-%d')
for (ii in startyear[num]:2021){
wateryear <- ii
wydf <- crossdf[which(crossdf$WY==wateryear),]
year.char <- as.character(wateryear-2000)


rsd <- comp.df[site,paste0(year.char,'_RSD')]
if (rsd<265) {
  red <- rsd+100
} else {
  red <- 365
}

rflows <- wydf[which(wydf$wyday >= rsd & wydf$wyday < red),'qpatch']

RRM <- (rflows[1]-rflows[31])/(30*site.areas[num])

comp.df[site,paste0(year.char,'_RRM')] <- RRM
}}
paste("RRM Calculated for", sitename)

```

```{r}
write.csv(comp.df, paste0('C:/Users/Daniel/Documents/Research/data/dataframes/catchment_comparison.csv'), row.names = F)
paste('data for',sitename,'saved to catchment_comparison.csv at',date())
```

### Annual Metrics
--- Future baseflow t+1 (FBF)
```{r}
#num <- 1
for (num in 1:12){
  site <- sitecodes[num]               
sitename <- sitenames[num]
siteabv <- siteabbr[num]
sitenum <- num
crossdf <- read.csv(paste0('C:/Users/Daniel/Documents/Research/data/dataframes/patched_data/',site,'_patched.csv'))

crossdf$date <- as.Date(crossdf$date,'%Y-%m-%d')
#ii <- 2015
for (ii in startyear[num]:2020){ #can't do this for 2021 yet

wateryear <- ii
wydf <- crossdf[which(crossdf$WY==wateryear),]
year.char <- as.character(wateryear-2000)
next.year <- as.character(wateryear-2000+1)


#bsd <- comp.df[site,paste0(year.char,'_BSD')]
#msd <- comp.df[site,paste0(year.char,'_MSD')]

#bflows <- wydf[c(bsd:msd),'qpatch']

fbf <- comp.df[site,paste0(next.year,'_QRM')]

comp.df[site,paste0(year.char,'_FBF')] <- fbf
}}
paste("FBF Calculated for", sitename)
```

--- total fall rain (TFR) (from snotel)
```{r}
#num <- 1
for (num in 1:12){
  site <- sitecodes[num]               
sitename <- sitenames[num]
siteabv <- siteabbr[num]
sitenum <- num
crossdf <- read.csv(paste0('C:/Users/Daniel/Documents/Research/data/dataframes/patched_data/',site,'_patched.csv'))

crossdf$date <- as.Date(crossdf$date,'%Y-%m-%d')

for (ii in startyear[num]:2021){

wateryear <- ii
wydf <- crossdf[which(crossdf$WY==wateryear),]
year.char <- as.character(wateryear-2000)


bsd <- comp.df[site,paste0(year.char,'_BSD')]
msd <- comp.df[site,paste0(year.char,'_MSD')]

bflows <- wydf[c(bsd:msd),]

tfr <- sum(bflows$SWI , na.rm = T)

comp.df[site,paste0(year.char,'_TFR')] <- tfr
}}
paste("TFR Calculated for", sitename)
```

--- total modeled fall precip (TMP))
```{r}
#num <- 1
for (num in c(1:5,12)){
  site <- sitecodes[num]               
sitename <- sitenames[num]
siteabv <- siteabbr[num]
sitenum <- num
crossdf <- read.csv(paste0('C:/Users/Daniel/Documents/Research/data/dataframes/',site,'_mod.csv'))

crossdf$date <- as.Date(crossdf$date,'%Y-%m-%d')

for (ii in startyear[num]:2018){

wateryear <- ii
wydf <- crossdf[which(crossdf$WY==wateryear),]
year.char <- as.character(wateryear-2000)


bsd <- comp.df[site,paste0(year.char,'_BSD')]
msd <- comp.df[site,paste0(year.char,'_MSD')]

bflows <- wydf[c(bsd:msd),]

tmp <- sum(bflows$SWIT , na.rm = T)

comp.df[site,paste0(year.char,'_TMP')] <- tmp
}}
paste("TMP Calculated for", sitename)
```

--- mean annual discharge (QAV)
```{r}
#num <- 1
for (num in 1:12){
  site <- sitecodes[num]               
sitename <- sitenames[num]
siteabv <- siteabbr[num]
sitenum <- num
crossdf <- read.csv(paste0('C:/Users/Daniel/Documents/Research/data/dataframes/patched_data/',site,'_patched.csv'))

crossdf$date <- as.Date(crossdf$date,'%Y-%m-%d')

for (ii in startyear[num]:2021){

wateryear <- ii
wydf <- crossdf[which(crossdf$WY==wateryear),]
year.char <- as.character(wateryear-2000)


#bsd <- comp.df[site,paste0(year.char,'_BSD')]
#msd <- comp.df[site,paste0(year.char,'_MSD')]

#bflows <- wydf[c(bsd:msd),'qpatch']

qav <- mean(wydf$qpatch, na.rm = T)

comp.df[site,paste0(year.char,'_QAV')] <- qav}}
paste("QAV Calculated for", sitename)
```

--- Modeled runoff ratio (RRS)
```{r}
#num <- 1
for (num in c(1:5,12)){
  site <- sitecodes[num]               
sitename <- sitenames[num]
siteabv <- siteabbr[num]
sitenum <- num
crossdf <- read.csv(paste0('C:/Users/Daniel/Documents/Research/data/dataframes/',site,'_mod.csv'))

crossdf$date <- as.Date(crossdf$date,'%Y-%m-%d')

for (ii in startyear[num]:2018){

wateryear <- ii
wydf <- crossdf[which(crossdf$WY==wateryear),]
year.char <- as.character(wateryear-2000)


totalQ <- sum(wydf$qpatch)/site.areas[num]*3.6*24
totalSWIT <- sum(wydf$SWIT)*1000



rrs <- totalQ/totalSWIT

comp.df[site,paste0(year.char,'_RRS')] <- rrs
}}
paste("RRS Calculated for", sitename)
```

--- Max SWE (mm) (MXS) from UEB
```{r}
#num <- 1
for (num in c(1:5,12)){
  site <- sitecodes[num]               
sitename <- sitenames[num]
siteabv <- siteabbr[num]
sitenum <- num
crossdf <- read.csv(paste0('C:/Users/Daniel/Documents/Research/data/dataframes/',site,'_mod.csv'))

crossdf$date <- as.Date(crossdf$date,'%Y-%m-%d')

for (ii in startyear[num]:2018){

wateryear <- ii
wydf <- crossdf[which(crossdf$WY==wateryear),]
year.char <- as.character(wateryear-2000)


#bsd <- comp.df[site,paste0(year.char,'_BSD')]
#msd <- comp.df[site,paste0(year.char,'_MSD')]

#bflows <- wydf[c(bsd:msd),'qpatch']

mxs <- max(wydf$SWE, na.rm = T)

comp.df[site,paste0(year.char,'_MXS')] <- mxs
}}
paste("MXS Calculated for", sitename)
```

--- Q|SWIT lag to peak of correlation (QFP)
```{r}

for (num in 1:5){
  site <- sitecodes[num]               
sitename <- sitenames[num]
siteabv <- siteabbr[num]
sitenum <- num
crossdf <- read.csv(paste0('C:/Users/Daniel/Documents/Research/data/dataframes/',site,'_mod.csv'))

crossdf$date <- as.Date(crossdf$date,'%Y-%m-%d')

for (ii in startyear[num]:2018){
lagmax <- 60
wateryear <- ii
wydf <- crossdf[which(crossdf$WY==wateryear),]
year.char <- as.character(wateryear-2000)

msd <- comp.df[site,paste0(year.char,'_MSD')]-30
rsd <- comp.df[site,paste0(year.char,'_RSD')]+60

mflows <- wydf[which(wydf$wyday >= msd & wydf$wyday < rsd),]


mccf <- ccf(mflows$qpatch, mflows$SWIT, lag.max = lagmax, 
             plot = F, na.action = na.pass)

lagmax <- max(mccf$lag)

QFP <- mccf$lag[which(mccf$acf==max(mccf$acf[(lagmax+1):(2*lagmax+1)]))]

comp.df[site,paste0(year.char,'_QFP')] <- QFP
}}
paste("QFP Calculated for", sitename)

```

--- Save dataframe
```{r}
write.csv(comp.df, paste0('C:/Users/Daniel/Documents/Research/data/dataframes/catchment_comparison.csv'), row.names = F)
paste('data for',sitename,'saved to catchment_comparison.csv at',date())
```


### Area-outlet normalized metrics
```{r}
metric <- 'QRM'
vals.df <- comp.df[,which(substr(colnames(comp.df),4,6)==metric)]
vals.df
```
```{r}
year <- 15
year.df <- vals.df[,which(substr(colnames(vals.df),1,2)==as.character(year))]
year.df/year.df[12]
```
```{r}
for (i in 1:ncol(vals.df)) {
vals.df[,i] <- vals.df[,i]/vals.df[12,i]
}
vals.df
```
```{r}
AOmets <- data.frame(AOmets,vals.df)
```


### Other old stuff
count total entries for each water year
```{r}
wateryears <- crossdf$WY[which(crossdf$wyday==1)]
wateryears
sum(crossdf$WY==2015)
sum(crossdf$WY==2016)
sum(crossdf$WY==2017)
sum(crossdf$WY==2018)

```

Calculate total SWIT
```{r}
paste('Annual water input totals for', sitename)
paste(2015, sum(crossdf$SWIT[which(crossdf$WY==2015)]))
paste(2016, sum(crossdf$SWIT[which(crossdf$WY==2016)]))
paste(2017, sum(crossdf$SWIT[which(crossdf$WY==2017)]))
paste(2018, sum(crossdf$SWIT[which(crossdf$WY==2018)]))
```

```{r}
paste('discharge (cubic m) totals for', sitename)
paste(2015, mean(crossdf$qpatch[which(crossdf$WY==2015)])*31536000)
paste(2016, mean(crossdf$qpatch[which(crossdf$WY==2016)])*31622400)
paste(2017, mean(crossdf$qpatch[which(crossdf$WY==2017)])*31536000)
paste(2018, mean(crossdf$qpatch[which(crossdf$WY==2018)])*31536000)
```


```{r}
paste('discharge (m) totals for', sitename)
paste(2015, mean(crossdf$qpatch[which(crossdf$WY==2015)])*31536000/siteareas[i])
paste(2016, mean(crossdf$qpatch[which(crossdf$WY==2016)])*31622400/siteareas[i])
paste(2017, mean(crossdf$qpatch[which(crossdf$WY==2017)])*31536000/siteareas[i])
paste(2018, mean(crossdf$qpatch[which(crossdf$WY==2018)])*31536000/siteareas[i])
```
### Save the comp.df dataframe
--- Save dataframe
```{r}
write.csv(comp.df, paste0('C:/Users/Daniel/Documents/Research/data/dataframes/catchment_comparison.csv'), row.names = F)
paste('data for',sitename,'saved to catchment_comparison.csv at',date())
```