---
title: "NWIS Data Retrieval"
author: "Daniel Thurber"
date: "8/27/2021"
output: pdf_document
---
```{r}
library(dataRetrieval)
library(snotelr)
```


Enter site names and codes for USGS gauge and NRCS SNOTEL station ID numbers
```{r}
basin.name <- 'Sunlight Creek' #user input
gaugenum <- '06206500' #user input
snoname <- 'Evening Star' #user input
snosite <- 472 #user input
snodf1 <- snotel_download(site_id = snosite, internal = T)
snosite.meta <- snodf1[1,]
snosite.meta
```

Create a new dataframe with only the relevant variables
```{r}
snodf <- data.frame(date = snodf1$date,
                  SWE_mm = snodf1$snow_water_equivalent,
                  precip_mm = snodf1$precipitation)
snodf$date <- as.Date(snodf$date,'%Y-%m-%d')
head(snodf,3)
```


Add water year info
```{r}
snodf$day <- format(as.Date(snodf$date),'%m-%d')

wydates <- data.frame(wyday = seq(1,366),
day=format(seq.Date(as.Date('2019-10-1','%Y-%m-%d'),as.Date('2020-09-30','%Y-%m-%d'),1),'%m-%d'))

for (i in 1:nrow(snodf)){
  snodf$wyday[i] <- wydates$wyday[which(wydates$day==snodf$day[i])]
}
snodf$WY = ifelse(as.numeric(format(snodf$date,'%m'))>=10, 
                     as.numeric(format(snodf$date,'%Y'))+1, 
                     as.numeric(format(snodf$date,'%Y'))) #determine water year
head(snodf,3)
```

generate columns for rain and melt based on precip and SWE changes.
```{r}
snodf$melt = 0
for (i in 1:nrow(snodf)){ #calculate and report daily melt
  snodf$melt[i] = max(0,snodf$SWE_mm[i-1]-snodf$SWE_mm[i]) 
}
snodf$rain=0
for (i in 1:nrow(snodf)){ #calculate and report daily rain
  snodf$rain[i] = round(max(0,snodf$precip_mm[i]-max(0,snodf$SWE_mm[i+1]+snodf$SWE_mm[i])),2) 
}
snodf$swi=snodf$melt+snodf$rain
```

```{r}
pholes <- which(is.na(snodf$precip))
sholes <- which(is.na(snodf$SWE))
tail(pholes)
tail(sholes)
```


```{r}
plot(snodf$SWE, type = 'l', ylab = 'SWE (mm)',
     main = paste('SWE at', snoname))
abline(v = sholes, col = 'red')

plot(snodf$precip, type = 'l', ylab = 'precip (mm)',
     main = paste('Precip at', snoname))
abline(v = pholes, col = 'red')
```
find the index first water year that is completely covered with snotel data
```{r}
tail(sholes,10) #NA values for SWE
tail(pholes,10) #NA values for precip
paste('start of WY:')
head(which(snodf$wyday==1)) #rows that correspond to the start of a water year
```
Enter the index of the first WY=1 row to double check
```{r}
snodf$date[731]
```

Based on the end of NA data, choose the first day in a long sequence of intact data

```{r}
a <- 731 #first value to keep (user input for each round)
b <- a+350 #approx one year after a
barplot(snodf$precip_mm[a:b], axes = F)
axis(side = 4, at = pretty(range(snodf$precip[a:b]), n = 4))

par(new=T)
yrange = range(snodf$SWE_mm[a:b], na.rm = T)
#plot discharge over the window.  The line gets plotted later over the highlight rectangles
plot(snodf$SWE_mm, xlim = c(a, b), ylim = yrange, type = 'l', ylab = 'SWE (mm)', 
     main = paste('SWE & precip at', snoname,snodf$WY[a]), xaxt = 'n', xlab = 'date'
     )
axis(1, at = seq(a,b, length.out = 6), labels = (snodf$date[seq(a,b,length.out = 6)]))
lines(snodf$swi*6, col = 'red')
```

If the plot looks alright, use this code chunk once to create a new dataframe
```{r}
 #rows to trim off the front end, one less than the first water year day 1 
snoflo= data.frame(snodf[-seq(1,a-1),], row.names = seq(1,nrow(snodf)-a+1))
a <- NA
```

```{r}
if (a==1) {
  snoflo= snodf
  
} else {
  snoflo= data.frame(snodf[-seq(1,a-1),], row.names = seq(1,nrow(snodf)-a+1))
  a <- NA
}
```


Run this chunk to download flow data on daily time steps starting with the first date of snotel data
```{r}
# Select a USGS gage ID. 
SiteNumber = as.numeric(gaugenum)        # Site ID

#activate the next line if the gauge number is 8 digits with a leading zero
SiteNumber = formatC(SiteNumber, width = 8, flag = 0, format = 'd')
ParamCode  = "00060"           # The code for the discharge
StatCode   = "00003"           # The code for the average values
Start_Date = as.character(snoflo$date[1])      # Start date, format: YYYY-MM-DD
End_Date   = "2020-09-30"      # End date, format: YYYY-MM-DD
Daily_Q = readNWISdv(SiteNumber, ParamCode, Start_Date, End_Date, StatCode)
gauge.meta <- Daily_Q[1,]
Daily_Q <- data.frame(date=Daily_Q$Date,
                      discharge = Daily_Q$X_00060_00003)
```

```{r}
snoflow <- merge(snoflo,Daily_Q, by= 'date', all = T)
head(snoflow)
```

```{r}
write.csv(snoflow, paste0('C:/Users/Daniel/Documents/Research/data/O2_time_series/',basin.name,'_',snoname,'.csv'))
#C:/Users/ERLgy/Downloads/WETlab/O2_time_series/
```


