---
title: "Data Patching"
author: "Daniel Thurber"
date: "7/2/2021"
output: pdf_document
---
initialize the session
```{r}
mypath <- 'C:/Users/Daniel/Documents/Research/data/dataframes/'  #leave this as directory
library(naniar)
library(snotelr)

sitecodes <- c('LR_FB_BA', 'LR_TG_BA', 'BC_CONF_A', 'TF_CONF_A','RHF_CONF_A', 'RS_CONF_A', 
               'TF_SAWM_A', 'SPC_CONF_A', 'LR_WC_A', 'LR_GCB_A', 'WCS_CONF_A', 'LR_FD')
sitenames <- c('Franklin Basin', 'Tony Grove', 'Beaver Creek', 'Temple Fork', 'Right Hand Fork','Ricks Spring', 
               'TF at Sawmill', 'Spawn Creek', 'Above Wood Camp', 'Guinavah Campground','Wood Camp Spring','First Dam')
siteabbr <- c('FB', 'TG', 'BC', 'TF','RH', 'RS', 
              'TS', 'SC', 'WC', 'GC', 'WS','FD')

sitesnotel <- c(1115, 1115, 1114,1013,1013, 823, 
              1013, 1098, 1113, 1113, 823,1098)
#FB_484, GCS_1114, KN_1115, TF_1013, TGL_823, TGRS_1113, UDD_1098

acf.sites <- c('FB_', 'TG_', 'BC_', 'TF_', 'RH_', 'RS_', 'TS_', 'SC_', 'WC_', 'GC_', 'WS_', 'FD_')
acf.years <- c('15','16','17','18','19','20','21')

linecols <- c('brown3', 'goldenrod', 'forestgreen', 'bisque4', 'slateblue', 'tan1', 
              'aquamarine3', 'magenta4', 'sienna3','cyan','violetred2','yellow2')
linetypes <- c(1,1,1,1,1,3,1,1,1,1,4,1)
rgbmat <- col2rgb(linecols)
wydates <- data.frame(wyday = seq(1,366),
day=format(seq.Date(as.Date('2019-10-1','%Y-%m-%d'),as.Date('2020-09-30','%Y-%m-%d'),1),'%m-%d'))
```



Select a site by index number
```{r}
i <- 1
site <- sitecodes[i]               #enter site code for file upload and export
sitename <- sitenames[i]        #enter site name for plotting
paste('Site:', sitecodes[i], '-', sitenames[i])
snosite <- sitesnotel[i]
   #the line color vector is used by other plotting scripts as well.  Attempt to keep it consistent
crossdf <- read.csv(paste0('C:/Users/Daniel/Documents/Research/data/dataframes/patched_data/',site,'_patched.csv'))

```

### open and append dataframe for a selected site
If you are re-opening a previously patched file, do so with this chunk
```{r}
crossdf <- read.csv(paste0('C:/Users/Daniel/Documents/Research/data/dataframes/patched_data/',site,'_patched.csv'))
crossdf$date <- as.Date(crossdf$date,'%Y-%m-%d')
#crossdf$date <- as.Date(crossdf$date,'%m/%d/%Y')

range(crossdf$date)
colnames(crossdf)
nrow(crossdf)
```


---Add a water year columns to the dataframe as needed
```{r}
crossdf$WY = ifelse(as.numeric(format(crossdf$date,'%m'))>=10, 
                     as.numeric(format(crossdf$date,'%Y'))+1, 
                     as.numeric(format(crossdf$date,'%Y'))) #determine water year
```

```{r}
crossdf$day <- format(as.Date(crossdf$date),'%m-%d')
crossdf$wyday <- 0
head(crossdf[tail(colnames(crossdf))],3)

```

Populate water year day column with appropriate values 1-366
```{r}
for (i in 1:nrow(crossdf)){
  crossdf$wyday[i] <- wydates$wyday[which(wydates$day==crossdf$day[i])]
}
head(crossdf[tail(colnames(crossdf))],3)
```


--- visualize and continue
```{r}
plot(crossdf$cpatch, type = 'l', main = paste('patched conductance at',sitename))

plot(crossdf$qpatch, type = 'l', main = paste('patched discharge at',sitename))

```


---Trim end of dataframe
Look at specific values and the first positions of NA values
```{r}
a <- 2400
b <- 2500
crossdf$qpatch[a:b]
head(which(is.na(crossdf$qpatch)))
```

select an index range (based on plot above) and see if the interval looks good.  Red lines are drawn on NA values
```{r}
keep.rows <- 1:nrow(crossdf)
keep.rows <- 1:2387 #comment out to keep all
plot(crossdf$cpatch[keep.rows], type = 'l', ylab = 'conductance',
     main = paste(sum(is.na(crossdf$cpatch[keep.rows])),'missing conductance values'))
abline(v = which(is.na(crossdf$cpatch[keep.rows])), col = 'red')

plot(crossdf$qpatch[keep.rows], type = 'l', xlim = range(keep.rows), ylab = 'discharge',
     main = paste(sum(is.na(crossdf$qpatch[keep.rows])),'missing discharge values'))
abline(v = which(is.na(crossdf$qpatch[keep.rows])), col = 'red')

```

Trim the dataframe and plot result.  Unpatched values are indicated by red lines.
```{r}
new.cross <- crossdf[keep.rows,]
plot(new.cross$qpatch, type = 'l', main = paste('discharge at', sitename))
abline(v = which(is.na(new.cross$qpatch)), col = 'red')

```


--- prepare new data to append

Open updated data and compare range to existing patched data
```{r}
new.data <- read.csv(paste0('C:/Users/Daniel/Documents/Research/data/new_LRO_aquatic/',site,'.csv'))
new.data$date <- as.Date(new.data$date,'%Y-%m-%d')
paste('patched data range:')
range(new.cross$date)
paste('new data range:')
range(new.data$date)

```

Compare patched data to new observations
```{r}
plot(new.data$discharge, type = 'l', main = paste('Discharge at', sitename), ylab = 'discharge')
lines(new.cross$qpatch, type = 'l', col = 'cadetblue2') #will only overlap if start dates line up
legend('topright', col = c( 'cadet blue2','black'),lty = 1, legend = c('downladed May \'21','downloaded Jan \'22'))
```

identify end of current data.  Appending will start here
```{r}
cross.start <- new.cross$date[1]
cross.end <- new.cross$date[nrow(new.cross)]
cross.end
```

create data to append, sync column names (temp, cpatch, qpatch)
```{r}
append.df <- new.data[which(new.data$date>cross.end),]
range(append.df$date)
colnames(append.df)
colnames(append.df)[which(colnames(append.df) == 'temperature')] <- 'temp'
append.df$cpatch <- append.df$conductance
append.df$qpatch <- append.df$discharge
colnames(append.df)
```

check for present/missing columns.  all columns from append should be in new.cross, append should be missing melt, rain, and SWI
```{r}
data.frame('column name' = colnames(new.cross),
'in_append.df' = colnames(new.cross) %in% colnames(append.df))

data.frame('column name' = colnames(append.df),
'in_new.cross' = colnames(append.df) %in% colnames(new.cross))
```


--- add missing data for snotel
```{r}
snodf <- snotel_download(site_id = snosite, internal = T)
snosite.meta <- snodf[1,]
snosite.meta
```

Keep and rename relevant variables
```{r}
snodf <- data.frame(date = snodf$date,
                  SWE_mm = snodf$snow_water_equivalent,
                  precip_mm = snodf$precipitation)
snodf$date <- as.Date(snodf$date,'%Y-%m-%d')
head(snodf,3)
```


Add water year info
```{r}
snodf$day <- format(as.Date(snodf$date),'%m-%d')

for (i in 1:nrow(snodf)){
  snodf$wyday[i] <- wydates$wyday[which(wydates$day==snodf$day[i])]
}
snodf$WY = ifelse(as.numeric(format(snodf$date,'%m'))>=10, 
                     as.numeric(format(snodf$date,'%Y'))+1, 
                     as.numeric(format(snodf$date,'%Y'))) #determine water year
head(snodf,3)
```

generate columns for rain and melt based on precip and SWE changes.
```{r}
snodf$melt = 0
for (i in 1:nrow(snodf)){ #calculate and report daily melt
  snodf$melt[i] = max(0,snodf$SWE_mm[i-1]-snodf$SWE_mm[i]) 
}
snodf$rain=0
for (i in 1:nrow(snodf)){ #calculate and report daily rain
  snodf$rain[i] = round(max(0,snodf$precip_mm[i]-max(0,snodf$SWE_mm[i+1]+snodf$SWE_mm[i])),2) 
}
snodf$swi=snodf$melt+snodf$rain
```

list the most recent rows with NA data
```{r}
pholes <- which(is.na(snodf$precip))
sholes <- which(is.na(snodf$SWE))
tail(pholes)
tail(sholes)
```

keep only relevant new variables
```{r}
snodf <- snodf[c('date','melt','rain','swi')]
colnames(snodf)[4] <- 'SWI'
head(snodf,3)
```
Make a quick plot of the final 365 observations, making sure rain, melt, and SWI have values
```{r}
plot(tail(snodf$SWI,365), type = 'l', lwd = 2)
lines(tail(snodf$rain,365), col = linecols[1])
lines(tail(snodf$melt,365), col = linecols[2])
legend('topright', legend = c('rain', 'melt'), lty = 1, col = linecols[1:2])
```


add snow data to data for appending
```{r}
append.df <- merge(x = append.df, y = snodf, by = 'date')
```



--- actually append dataframe
identify and indicate missing columns (should output "character (0)")
```{r}
missing.cols <- colnames(new.cross)[which(colnames(new.cross) %in% colnames(append.df)==F)]
missing.cols
```
add blank columns to enable append (typically unnecessary)
```{r}
append.df[,missing.cols]=NA

head(append.df[tail(colnames(append.df))],3)
```

combine and check column names match with new.cross, but not append.df
```{r}
crossdf <- rbind(new.cross,append.df)
colnames(crossdf)==colnames(new.cross)
colnames(append.df)==colnames(new.cross)
```

check that values match from append.df to crossdf
```{r}
tail(crossdf[colnames(crossdf)])==tail(append.df[colnames(crossdf)])
```

save updated dataframe
```{r}
write.csv(crossdf, paste0('C:/Users/Daniel/Documents/Research/data/dataframes/patched_data/',site,'_patched.csv'), row.names = F)
```


--- original code for adding snotel data
Begin by running SNOTEL and LRO_aquatic scripts to generate the qtc and snodf dataframes as .csv files.  This chunk will re-open them.

```{r}
snofile <- 'TGL_823.csv'
#FB_484, GCS_1114, KN_1115, TF_1013, TGL_823, TGRS_1113, UDD_1098

qtc <- read.csv(paste0(mypath,site,'.csv'), stringsAsFactors = F)
snodf <- read.csv(paste0(mypath,snofile), stringsAsFactors = F)
qtc$date <- as.Date(qtc$date,'%Y-%m-%d')
snodf$Date = as.Date(snodf$Date, format = '%Y-%m-%d')
mindate <- qtc$date[1]
```

This chunk will compile the crossdf dataframe with columns for date, melt, rain, discharge, temp, and conductance
```{r}
crossdf <- data.frame(date = snodf$Date[which(snodf$Date==mindate):nrow(snodf)])
crossdf$melt = snodf$melt[which(snodf$Date==mindate):nrow(snodf)]
crossdf$rain = snodf$rain[which(snodf$Date==mindate):nrow(snodf)]
for (i in 1:nrow(qtc)){
  crossdf$discharge[which(crossdf$date == qtc$date[i])] = qtc$discharge[i]
}
for (i in 1:nrow(qtc)){
  crossdf$conductance[which(crossdf$date == qtc$date[i])] = qtc$conductance[i]
}
for (i in 1:nrow(qtc)){
  crossdf$temp[which(crossdf$date == qtc$date[i])] = qtc$temperature[i]
}
crossdf$SWI <- crossdf$melt+crossdf$rain

crossdf$cpatch <- crossdf$conductance
crossdf$qpatch <- crossdf$discharge
```


---

```{r}
qholes <- which(is.na(crossdf$qpatch))
mholes <- which(is.na(crossdf$melt))
choles <- which(is.na(crossdf$cpatch))

```


```{r}
paste('missing discharge:') 
qholes
paste('missing conductance:')
choles

```

###Patching Cycle starts here ----------
Generate plots 
```{r}
plot(crossdf$qpatch, type = 'l', ylab = 'discharge', main = paste('Discharge at', sitename))
abline(v = qholes, col = 'red')
abline(v = which(format(crossdf$date,'%m-%d')=='10-01'), col='goldenrod2')


plot(crossdf$cpatch, type = 'l', ylab = 'conductance', main = paste('Conductance at', sitename))
abline(v = choles, col = 'red')
abline(v = which(format(crossdf$date,'%m-%d')=='10-01'), col='goldenrod2')

plot(crossdf$qpatch, type = 'l', ylab = 'discharge', main = paste('Discharge at', sitename),
     xaxt = 'n', xlab = '')
abline(v = qholes, col = 'red')
abline(v = which(format(crossdf$date,'%m-%d')=='10-01'), col='goldenrod2')
axis(1, at = seq(1,nrow(crossdf), length.out = 7), 
     labels = (crossdf$date[seq(1,nrow(crossdf),length.out = 7)]))

#plot(crossdf$melt, type = 'l', ylab = 'Melt', main = paste('melt at', sitename))
#abline(v = mholes, col = 'red')
```
Conductance
--- 

Create plot of patched time series and highlight the holes in data (red) and patches (green)
```{r}
#plot(crossdf$qpatch, type = 'l', ylab = 'discharge', main = paste('Patched discharge at', sitename))
#abline(v = qholes, col = 'red')

plot(crossdf$cpatch, type = 'n', ylab = 'conductance', main = paste('Patched Conductance at', sitename))
abline(v = which(is.na(crossdf$conductance)), col = 'seagreen2')
abline(v = choles, col = 'red')
abline(v = which(format(crossdf$date,'%m-%d')=='10-01'), col='goldenrod2')
lines(crossdf$cpatch)

#plot(crossdf$melt, type = 'l', ylab = 'Melt', main = paste('melt at', sitename))
#abline(v = mholes, col = 'red')
```

Zoom in on a section of the conductance plot worth patching



```{r}
patch.int <- c(2130, 2185)

#patch.rng <- range(crossdf$cpatch[patch.int[1]:patch.int[2]], na.rm = T)
#choles

patch.rng <- range(crossdf$cpatch[patch.int[1]:patch.int[2]], na.rm = T)
crossdf$date[mean(patch.int)]
choles

plot(crossdf$cpatch, xlim=patch.int, type= 'l', main = paste(sitename,'centered at',crossdf$date[mean(patch.int)]), ylab = 'conductance')
abline(v = choles, col = 'red')

#plot(crossdf$qpatch, xlim=patch.int, type= 'l', main = sitename, ylab = 'discharge')
#abline(v = qholes, col = 'red')

```

for single patches, run this chunk and enter the index (in console) to interpolate
```{r}
spike <- as.integer(readline(prompt = "Enter index to patch:")) #enter prompt in console
crossdf$cpatch[spike] <- mean(crossdf$cpatch[(spike-1):(spike+1)], na.rm = T) #range can be adjusted
choles <- which(is.na(crossdf$cpatch))
```

find the length of the patch
```{r}
patch.len <-  sum(is.na(crossdf$cpatch[patch.int[1]:patch.int[2]]))
i1 <- 1 #first index of choles to consider
i2 <- 13 #final value of choles to consider
i2 <- i1-1+patch.len
patch.len 
paste('replace from index', choles[i1], 'to', choles[i2])
```


Generate and insert a horizontal noise patch. 
```{r}
patchvals <- runif(i2-i1+1,patch.rng[1], patch.rng[2])  
#patch.rng represents the range of values over the surrounding interval
crossdf$cpatch[choles[i1]:choles[i2]] = patchvals
i1 <- NA
i2 <- NA
plot(crossdf$cpatch, xlim=patch.int, type= 'l', ylab = 'conductance', 
     main = paste('conductance at', sitename), col = 'seagreen2')
lines(crossdf$conductance, xlim=patch.int)

```

Generate and insert a linear patch
```{r}
patchvals <- seq(crossdf$cpatch[choles[i1]-1],
                 crossdf$cpatch[choles[i2]+1],
                 length.out = i2-i1+3)
crossdf$cpatch[(choles[i1]-1):(choles[i2]+1)] = patchvals
i1 <- NA
i2 <- NA
plot(crossdf$cpatch, xlim=patch.int, type= 'l', ylab = 'conductance', 
     main = paste('conductance at', sitename), col = 'seagreen2')
lines(crossdf$conductance, xlim=patch.int)

```


If there was a problem, set up this chunk to undo it (set indices to replace cpatch):
```{r}
j <- patch.int[1]
k <- patch.int[2]

crossdf$cpatch[j:k]=crossdf$conductance[j:k]

```

If it looks good, reset the choles vector
```{r}
choles <- which(is.na(crossdf$cpatch))
choles

```


Save the dataframe for continuation later
```{r}
write.csv(crossdf, paste0('C:/Users/Daniel/Documents/Research/data/dataframes/patched_data/',site,'_patched.csv'), row.names = F)
```



Discharge
---
Create plots of patched time series and highlight the holes in data
```{r}
date.mark <- '04-01' #vertical blue lines will be drawn at this date for reference
plot(crossdf$qpatch, type = 'n', ylab = 'discharge', main = paste('Patched discharge at', sitename))
abline(v = which(is.na(crossdf$discharge)), col = 'seagreen2')
abline(v = qholes, col = 'red')
lines(crossdf$qpatch)
abline(v = which(format(crossdf$date,'%m-%d')==date.mark), col='goldenrod2')

lines(crossdf$discharge1)

#add lines on the defined date to delineate water years
#abline(v = which(format(crossdf$date,'%m-%d')==date.mark), col='cadetblue')

#rgb(78,238,148, alpha = 0, maxColorValue = 255)
```

```{r}
which(format(crossdf$date,'%m-%d')=='11-01')
which(format(crossdf$date,'%m-%d')=='03-15')
```


Zoom in on a section of the discharge plot worth patching.  This chunk includes a protocol that can be used to replace spikes from ice damming with NA if necessary

```{r}
patch.int <- c(995,1013)
na.thresh <- 01

patch.rng <- range(crossdf$qpatch[patch.int[1]:patch.int[2]], na.rm = T)
#qholes

plot(crossdf$qpatch, xlim=patch.int, ylim = c(0,max(crossdf$qpatch[patch.int[1]:patch.int[2]], na.rm = T)),
     type= 'l', main = paste(sitename,'centered at',crossdf$date[mean(patch.int)]), 
     ylab = 'discharge', col = 'seagreen2')
abline(v = qholes, col = 'red')
#abline(h = na.thresh, lty = 3)
lines(crossdf$discharge)
#abline(v = frozen, col = 'goldenrod')
```

--- the next two chunks remove original values exceeding the threshold defined above
```{r}
spikes <- which(crossdf$qpatch>na.thresh)
frozen <- spikes[which(spikes>patch.int[1]&spikes<patch.int[2])]
frozen

```

replace spiked values with NA
```{r}
crossdf$qpatch[frozen] <- NA
qholes <- which(is.na(crossdf$qpatch))

```

--- for single patches, enter the index (in console) to interpolate
```{r}
spike <- as.integer(readline(prompt = "Enter index to patch:")) #enter prompt in console
crossdf$qpatch[spike] <- mean(crossdf$qpatch[(spike-1):(spike+1)], na.rm = T) #range can be adjusted
qholes <- which(is.na(crossdf$qpatch))
```

---

find the length of the patch.  Check the third outcome is "TRUE"
```{r}
patch.len <-  sum(is.na(crossdf$qpatch[patch.int[1]:patch.int[2]]))
i1 <- 1 #first index of qholes to consider
i2 <- 20 #final value of qholes to consider
i2 <- i1-1+patch.len
patch.len 
paste('replace from index', qholes[i1], 'to', qholes[i2])
qholes[i2]-qholes[i1]+1-patch.len==0  #this should read TRUE, meaning only one data gap exists
```


-----------------Generate and insert a horizontal noise patch. 
```{r}
patchvals <- runif(i2-i1+1,patch.rng[1], patch.rng[2])  
#patch.rng represents the range of values over the surrounding interval
crossdf$qpatch[qholes[i1]:qholes[i2]] = patchvals
i1 <- NA
i2 <- NA
plot(crossdf$qpatch, xlim=patch.int, type= 'l', ylab = 'Discharge', main = sitename, 
     ylim = c(0,max(crossdf$qpatch[patch.int[1]:patch.int[2]], na.rm = T)), col = 'seagreen2', xlab = 'date', xaxt = 'n')
lines(crossdf$discharge, xlim=patch.int)
axis(1, at = seq(patch.int[1], patch.int[2], length.out = 6), 
     labels = (crossdf$date[seq(patch.int[1], patch.int[2],length.out = 6)]))


plot(crossdf$qpatch, xlim=patch.int, type= 'l', ylab = 'Discharge', 
     main = sitename, ylim = c(0,max(crossdf$qpatch[patch.int[1]:patch.int[2]], na.rm = T)), col = 'seagreen2')
lines(crossdf$discharge, xlim=patch.int)

```




--------------Generate and insert a linear patch
```{r}
patchvals <- seq(crossdf$qpatch[qholes[i1]-1],
                 crossdf$qpatch[qholes[i2]+1],
                 length.out = i2-i1+3)
crossdf$qpatch[(qholes[i1]-1):(qholes[i2]+1)] = patchvals
i1 <- NA
i2 <- NA
plot(crossdf$qpatch, xlim=patch.int, type= 'l', ylab = 'Discharge', main = sitename, 
     ylim = c(0,max(crossdf$qpatch[patch.int[1]:patch.int[2]], na.rm = T)), col = 'seagreen2', xlab = 'date', xaxt = 'n')
lines(crossdf$discharge, xlim=patch.int)
axis(1, at = seq(patch.int[1], patch.int[2], length.out = 6), 
     labels = (crossdf$date[seq(patch.int[1], patch.int[2],length.out = 6)]))


plot(crossdf$qpatch, xlim=patch.int, type= 'l', ylab = 'Discharge', 
     main = sitename, ylim = c(0,max(crossdf$qpatch[patch.int[1]:patch.int[2]], na.rm = T)), col = 'seagreen2')
lines(crossdf$discharge, xlim=patch.int)

```



If there was a problem, try running this chunk to undo it (set a range over which to restore original values)
```{r}
j <- 
k <- 

crossdf$qpatch[j:k]=crossdf$discharge[j:k]

```


If it looks good, reset the qholes vector
```{r}
qholes <- which(is.na(crossdf$qpatch))
qholes[1:70]

```


###Save the dataframe for continuation later
```{r}
write.csv(crossdf, paste0('C:/Users/Daniel/Documents/Research/data/dataframes/patched_data/',site,'_patched.csv'), row.names = F)
```

---


```{r}
study.int <- c(220,450)
plot(crossdf$melt, xlim = study.int, type = 'l', main = sitename)
plot(crossdf$discharge, xlim = study.int, type = 'l', 
     main = paste('Discharge at',sitename))
abline(v = qholes, col = 'red')

plot(crossdf$conductance, xlim = study.int, type = 'l', ylab = 'Conductance', 
     main = paste('Conductance at', sitename))
abline(v = choles, col = 'red')
```


```{r}
win1 <- c(study.int[1],300)
win2 <- c(study.int[1],330)
win3 <- c(study.int[1],study.int[2])
win4 <- c(260,study.int[2])
win5 <- c(310,study.int[2])
plot(crossdf$discharge, xlim = study.int,
     type = 'n', ylab = '')

rect(xleft=win1[1], xright=win1[2], ybottom = 0, ytop=.2*yrange[2],  col = linecols[1])
rect(xleft=win2[1], xright=win2[2], ybottom = .2*yrange[2], ytop=.4*yrange[2],  col = linecols[2])
rect(xleft=win3[1], xright=win3[2], ybottom = .4*yrange[2], ytop=.6*yrange[2],  col = linecols[3])
rect(xleft=win4[1], xright=win4[2], ybottom = .6*yrange[2], ytop=.8*yrange[2],  col = linecols[4])
rect(xleft=win5[1], xright=win5[2], ybottom = .8*yrange[2], ytop=1*yrange[2],  col = linecols[5])

lines(crossdf$discharge[study.int[1]:study.int[2]])
```


```{r}
par(mar = c(5,4,4,4) + 0.3)
plot(crossdf$discharge[study.int[1]:study.int[2]], axes = F, type = 'n',
     xlab = '', ylab = '')

rect(xleft=win1[1], xright=win1[2], ybottom = 0, ytop=.2*yrange[2],  col = linecols[1])
rect(xleft=win2[1], xright=win2[2], ybottom = .2*yrange[2], ytop=.4*yrange[2],  col = linecols[2])
rect(xleft=win3[1], xright=win3[2], ybottom = .4*yrange[2], ytop=.6*yrange[2],  col = linecols[3])
rect(xleft=win4[1], xright=win4[2], ybottom = .6*yrange[2], ytop=.8*yrange[2],  col = linecols[4])
rect(xleft=win5[1], xright=win5[2], ybottom = .8*yrange[2], ytop=1*yrange[2],  col = linecols[5])

par(new = T)
barplot(crossdf$melt[study.int[1]:study.int[2]], ylab = 'melt (in)',
     main = paste('melt and discharge at', sitename), xlab = 'Date')
abline(v = qholes, col = 'red')
abline(v = study.int, lty =5)

par(new = T)
plot(crossdf$discharge[study.int[1]:study.int[2]], 
     type = 'l', axes = F, ylab = '', xlab = '')

axis(4, at = pretty(range(crossdf$discharge[study.int[1]:study.int[2]],na.rm = T)))
mtext("discharge (CMS)", side = 4, line = 3)
axis(1, at = seq(0,diff(study.int), length.out = 6), 
     labels = (crossdf$date[seq(study.int[1],study.int[2],length.out = 6)]))
```

```{r}
a <- study.int[1]  #index of starting time
#a <- 518
c <- 130  #window width (number of days)
b <- a+c    #calculates final index
b <- study.int[2]   #index of ending time
win1 <- c(a,300)
win2 <- c(a,360)
win3 <- c(a,b)
win4 <- c(300,b)
win5 <- c(360,b)
yrange <- c(0,max(qtc$discharge[a:b], na.rm = T))

#plot discharge over the window.  The line gets plotted later over the highlight rectangle
plot(qtc$discharge, xlim = c(a, b), ylim = yrange, type = 'n', ylab = 'discharge', 
     main = paste('discharge at', sitename), xaxt = 'n', xlab = 'date'
     )

#highlight ranges for each window of ACF analysis
rect(xleft=win1[1], xright=win1[2], ybottom = 0, ytop=.2*yrange[2],  col = linecols[1])
rect(xleft=win2[1], xright=win2[2], ybottom = .2*yrange[2], ytop=.4*yrange[2],  col = linecols[2])
rect(xleft=win3[1], xright=win3[2], ybottom = .4*yrange[2], ytop=.6*yrange[2],  col = linecols[3])
rect(xleft=win4[1], xright=win4[2], ybottom = .6*yrange[2], ytop=.8*yrange[2],  col = linecols[4])
rect(xleft=win5[1], xright=win5[2], ybottom = .8*yrange[2], ytop=1*yrange[2],  col = linecols[5])

#draw and annotate a box around any patches that exist.  Adjust numbers to position vertically
rect(patchstart, 0.5, patchend, 1.5)  #draw a box around patched section of line
text(mean(patchstart,patchend), 0.3, 'Patched values')  #annotate patch box

lines(lin.df$discharge, type = 'l', col = 'red')
lines(qtc$discharge, type = 'l')
axis(1, at = seq(a,b, length.out = 6), labels = (qtc$date[seq(a,b,length.out = 6)]))

```






### compile patched data into a single dataframe (all_LRO_sites.csv)
```{r}
siteabbr <- c('FB', 'TG', 'BC', 'TF','RH',
               'RS', 'TS', 'SC', 'WC', 'GC','WS')
i <- 11
site <- sitecodes[i]               #enter site code for file upload and export
sitename <- sitenames[i]        #enter site name for plotting
paste('Site:', sitecodes[i], '-', sitenames[i])
```
Read in the patched data for the site, view the data, and re-assign "site" to the abbreviated code
```{r}
site.df <- read.csv(paste0('C:/Users/Daniel/Documents/Research/data/dataframes/patched_data/',site,'_patched.csv'))
site.df$date <- as.Date(site.df$date,'%Y-%m-%d')
head(site.df)
site <- siteabbr[i]
```

Confine the dataframe to only LRO observed and patched data
```{r}
site.df <- site.df[c('date','discharge','conductance','temp','cpatch','qpatch')]
head(site.df, 3)
```

designate and print out new column names
```{r}
new.col.names <- c('date', paste0(site,'_Q'), paste0(site,'_C'), 
                   paste0(site,'_T'), paste0(site,'_CP'), paste0(site,'_QP'))
new.col.names
```

Assign new column names to the dataframe
```{r}
colnames(site.df)[which(colnames(site.df)=='discharge')] <- new.col.names[2]
colnames(site.df)[which(colnames(site.df)=='conductance')] <- new.col.names[3]
colnames(site.df)[which(colnames(site.df)=='temp')] <- new.col.names[4]
colnames(site.df)[which(colnames(site.df)=='cpatch')] <- new.col.names[5]
colnames(site.df)[which(colnames(site.df)=='qpatch')] <- new.col.names[6]
head(site.df, 3)
```
Merge the site data to the dataframe with all site data.  Print results should show a stable or increasing number of columns, a row of "FALSE", and a row of "TRUE"
```{r}
new.col.names[c(2:6)] %in% colnames(all.sites)
nrow(all.sites)
all.sites <- merge(all.sites, site.df, by = 'date', all = T)
site.df <- NULL
new.col.names %in% colnames(all.sites)
nrow(all.sites)

tail(colnames(all.sites))
```
Return to the top of the sequence and select a new site.

Save the dataframe
```{r}
write.csv(all.sites, 'C:/Users/Daniel/Documents/Research/data/dataframes/all_LRO_sites.csv',row.names = F)
```











