---
title: "Sensitivity Analyses"
author: "Daniel Thurber"
date: "7/2/2021"
output: pdf_document
---

```{r}
library(naniar)
library(ggplot2)
sitecodes <- c('LR_FB_BA', 'LR_TG_BA', 'BC_CONF_A', 'TF_CONF_A', 
               'RHF_CONF_A', 'RS_CONF_A')
sitenames <- c('Franklin Basin', 'Tony Grove', 'Beaver Creek', 'Temple Fork', 
               'Right Hand Fork', 'Ricks Spring')

linecols <- c('brown3', 'goldenrod', 'forestgreen', 'bisque4', 'slateblue', 'sienna3', 'aquamarine3', 'magenta4')

rgbmat <- col2rgb(linecols)/255
```


The following chunks explore the impact of anomalies within the original data on the ACF of 15-minute data
---

Create the qdf, tdf, and cdf objects.  This chunk is from LRO_aquatic.rmd.  This will read in original QC data with 15-min intervals.
```{r}
mypath <- 'C:/Users/Daniel/Documents/Research/data/LRO_aquatic/' #leave this directory alone!

i <-5

site <- sitecodes[i]               #enter site code for file upload and export
sitename <- sitenames[i]        #enter site name for plotting
paste('Site:', sitecodes[i], '-', sitenames[i])
maxT <- 100 #initially set these values high
maxC <- 1000 #they can be honed in later in the script

qfile <- paste0(site,'_Q.csv')
qdf <- read.csv(paste0(mypath,qfile), stringsAsFactors = F)
tfile <-  paste0(site,'_T.csv')
tdf <- read.csv(paste0(mypath,tfile), stringsAsFactors = F)
cfile <-  paste0(site,'_SC.csv')
cdf <- read.csv(paste0(mypath,cfile), stringsAsFactors = F)

minQ <- 0.00                     #below these thresholds, values will be replaced with NA
minT <- 0
minC <- 0
maxQ <- 100
maxT <- 200
maxC <- 8000

qdf$date <- as.Date(qdf$DateTime, '%m / %d / %Y %H:%M')
qdf$discharge <- (as.numeric(qdf$Value))
qdf$discharge <- replace(qdf$discharge, qdf$discharge<minQ |qdf$discharge>maxQ, NA)


cdf$date <- as.Date(cdf$DateTime, '%m / %d / %Y %H:%M')
cdf$conductance <- (as.numeric(cdf$Value))
cdf$conductance <- replace(cdf$conductance, cdf$conductance<minC |cdf$conductance>maxC, NA)


tdf$date <- as.Date(tdf$DateTime, '%m / %d / %Y %H:%M')
tdf$temperature <- (as.numeric(tdf$Value))
tdf$temperature <- replace(tdf$temperature, tdf$temperature<minT | tdf$temperature>maxT, NA)


```






```{r}
a <- 50000  #index of starting time
c <- 30000  #window width (number of 15-min intervals)
b <- a+c    #calculates final index

#plot discharge over the window.  The line gets plotted later over the highlight rectangle
plot(qdf$discharge[a:b], type = 'n', ylab = 'discharge', 
     main = paste('discharge at', sitename), xaxt = 'n', xlab = 'date'
     )

#highlight the region we will zoom in on later
rect(xleft=12000, ybottom = 0, ytop=2, xright=13000, col = 'cadetblue2')
lines(qdf$discharge[a:b], type = 'l')
axis(1, at = seq(0,c, length.out = 6), labels = (qdf$date[seq(a,b,length.out = 6)]))

```

Plot the region highlighted above.
```{r}
plot(qdf$discharge[62000:63000], type = 'l', ylab = 'discharge')
adjdf <- qdf[62000:63000,]
nadf <- qdf[62000:63000,]
randdf <- qdf[62000:63000,]
plot(adjdf$discharge[480:530], type= 'l', ylab = 'discharge', 
     xaxt = 'n', xlab = '',main = 'QAQC Data')
axis(1, at = seq(0,50, length.out = 6), labels = (adjdf$DateTime[seq(480,530, length.out = 6)]))

```

Identify the region that needs to be patched.  Create three different types of patches and plot them
```{r}
adjdf$discharge[504:508] <- .33
plot(adjdf$discharge[490:510], type= 'l', ylab = 'discharge', main = 'constant replacement')
nadf$discharge[504:508] <- NA
plot(nadf$discharge[490:510], type= 'l', ylab = 'discharge', main = 'NA replacement')
randdf$discharge[504:508] <-  runif(5,.3138, .3863)
plot(randdf$discharge[490:510], type= 'l', ylab = 'discharge', main = 'random replacement')

```

Calculates ACF values of the original and all adjusted dataframes of the established window
```{r}
regacf <- acf(qdf$discharge[62000:63000], lag.max = 300, type = "correlation", plot = F, na.action = na.pass)
adjacf <- acf(adjdf$discharge, lag.max = 300, type = "correlation", plot = F, na.action = na.pass)
naacf <- acf(nadf$discharge, lag.max = 300, type = "correlation", plot = F, na.action = na.pass)
randacf <- acf(randdf$discharge, lag.max = 300, type = "correlation", plot = F, na.action = na.pass)

```

Plot all ACF functions together: QC 15-min data and patched versions
```{r}
plot(regacf$lag, regacf$acf, type = 'l', col='blue',
     ylab = 'Correlation', xlab = 'Lag (15-min steps)', ylim = c(0,1), 
     main = paste('Autocorrelation sensitivity: Right Hand Fork'))
lines(naacf$acf, col = 'brown4')
lines(adjacf$acf, col = 'green')
lines(randacf$acf, col = 'purple')
abline(h = 0.2, lty = 3)
legend(155,1, legend = c('QC data', 'constant replacement', 'NA replacement', 'random replacement'), 
       lty = 1, col = c('blue', 'green', 'brown4', 'purple'))
```



---


Below, we look at aggregated daily average values of discharge, conductance, and temperature and the effects of specific windows within the water year on the ACF
---
Create the qtc object (daily timestep).  This chunk is from other analysis scripts.  It will read in aggregated daily average dataframes. 
```{r}
mypath <- 'C:/Users/Daniel/Documents/Research/data/dataframes/'  #leave this as directory

i <- 1
site <- sitecodes[i]               #enter site code for file upload and export
sitename <- sitenames[i]        #enter site name for plotting
paste('Site:', sitecodes[i], '-', sitenames[i])
   #the line color vector is used by other plotting scripts as well.  Attempt to keep it consistent
linecols <- c('brown3', 'goldenrod', 'forestgreen', 'bisque4', 'slateblue', 'sienna3', 'aquamarine3', 'magenta4')

qtc <- read.csv(paste0(mypath,site,'.csv'), stringsAsFactors = F)

qtc$date <- as.Date(qtc$date,'%Y-%m-%d')
qtc$day <- format(as.Date(qtc$date),'%m-%d')
qtc$wyday <- 0
head(qtc,3)
```

Find holes in the time series
```{r}
qholes <- which(is.na(qtc$discharge))
qholes
```

plot the discharge series and highlight all missing values.  Using the plot, iteratively focus on a study interval.
```{r}
study.int <- c(200,300) #select the study interval here
plot(qtc$discharge, type = 'n', ylab = 'discharge')
rect(study.int[1], 0, study.int[2], 20, col = 'deepskyblue')
lines(qtc$discharge)
abline(v = qholes, col = 'red')
plot(qtc$discharge, type = 'l', xlim = study.int, ylim=c(0,1.2), ylab = 'discharge')
abline(v = qholes, col = 'red')
abline(v = study.int[1], lty = 4)
```
create a linear patch.  If there are no holes in the data, set patch start and patchend to the same value.  That will help ensure that later code chunks run properly.
```{r}
patchstart <- 763
patchend <- 763
patchlength <- patchend - patchstart +1
linpatch <- seq(qtc$discharge[patchstart],qtc$discharge[patchend], length.out= patchlength)

```

generate a new dataframe and patch missing data with linear interpolation
```{r}
lin.df <- qtc
lin.df$discharge[patchstart:patchend] <- linpatch
plot(lin.df$discharge, type = 'l', xlim = c(730,780), ylim=c(0,5), 
     ylab = 'discharge', main = paste(sitename, 'patched data'), col = 'red')
lines(qtc$discharge)
```


Look at the sensitivity of ACF functions to windowing within a water year
```{r}
a <- study.int[1]  #index of starting time
#a <- 518
c <- 130  #window width (number of days)
b <- a+c    #calculates final index
b <- study.int[2]   #index of ending time
win1 <- c(a,1000)
win2 <- c(a,1050)
win3 <- c(a,b)
win4 <- c(1000,b)
win5 <- c(1050,b)
yrange <- c(0,max(qtc$discharge[a:b], na.rm = T))

#plot discharge over the window.  The line gets plotted later over the highlight rectangle
plot(qtc$discharge, xlim = c(a, b), ylim = yrange, type = 'n', ylab = 'discharge', 
     main = paste('discharge at', sitename), xaxt = 'n', xlab = 'date'
     )

#highlight ranges for each window of ACF analysis
rect(xleft=win1[1], xright=win1[2], ybottom = 0, ytop=.2*yrange[2],  col = linecols[1])
rect(xleft=win2[1], xright=win2[2], ybottom = .2*yrange[2], ytop=.4*yrange[2],  col = linecols[2])
rect(xleft=win3[1], xright=win3[2], ybottom = .4*yrange[2], ytop=.6*yrange[2],  col = linecols[3])
rect(xleft=win4[1], xright=win4[2], ybottom = .6*yrange[2], ytop=.8*yrange[2],  col = linecols[4])
rect(xleft=win5[1], xright=win5[2], ybottom = .8*yrange[2], ytop=1*yrange[2],  col = linecols[5])

#draw and annotate a box around any patches that exist.  Adjust numbers to position vertically
rect(patchstart, 0.5, patchend, 1.5)  #draw a box around patched section of line
text(mean(patchstart,patchend), 0.3, 'Patched values')  #annotate patch box

lines(lin.df$discharge, type = 'l', col = 'red')
lines(qtc$discharge, type = 'l')
axis(1, at = seq(a,b, length.out = 6), labels = (qtc$date[seq(a,b,length.out = 6)]))

```

Compute ACF within each window. X.1 versions calculate off of patched data
```{r}
acf1 <- acf(qtc$discharge[win1[1]:win1[2]], lag.max = 50, 
            type = "correlation", plot = F, na.action = na.pass)
acf2 <- acf(qtc$discharge[win2[1]:win2[2]], lag.max = 50, 
            type = "correlation", plot = F, na.action = na.pass)
acf3 <- acf(qtc$discharge[win3[1]:win3[2]], lag.max = 50, 
            type = "correlation", plot = F, na.action = na.pass)
acf4 <- acf(qtc$discharge[win4[1]:win4[2]], lag.max = 50, 
            type = "correlation", plot = F, na.action = na.pass)
acf5 <- acf(qtc$discharge[win5[1]:win5[2]], lag.max = 50, 
            type = "correlation", plot = F, na.action = na.pass)
acf3.1 <- acf(lin.df$discharge[win3[1]:win3[2]], lag.max = 50, 
            type = "correlation", plot = F, na.action = na.pass)
acf4.1 <- acf(lin.df$discharge[win4[1]:win4[2]], lag.max = 50, 
            type = "correlation", plot = F, na.action = na.pass)
acf5.1 <- acf(lin.df$discharge[win5[1]:win5[2]], lag.max = 50, 
            type = "correlation", plot = F, na.action = na.pass)
```

```{r}
plot(acf1$lag, acf1$acf, type = 'l', col=linecols[1],
     ylab = 'Correlation', xlab = 'Lag (days)', ylim = c(0,1), xlim = c(0,30), 
     main = paste('Autocorrelation window sensitivity:', sitename))
lines(acf2$acf, col = linecols[2])
lines(acf3$acf, col = linecols[3])
lines(acf4$acf, col = linecols[4])
lines(acf5$acf, col = linecols[5])

abline(h = 0.2, lty = 3)

```

```{r}
plot(acf3$lag, acf3$acf, type = 'l', col=linecols[3],
     ylab = 'Correlation', xlab = 'Lag (days)', ylim = c(0,1), xlim = c(0,30),
     main = paste('Autocorrelation patch sensitivity:', sitename))
lines(acf3.1$acf, col = linecols[3], lty = 2)

lines(acf4$acf, col = linecols[4])
lines(acf4.1$acf, col = linecols[4], lty = 2)

lines(acf5$acf, col = linecols[5])
lines(acf5.1$acf, col = linecols[5], lty = 2)

abline(h = 0.2, lty = 3)

legend('topright', legend = c('QC data', 'patched data'), lty = c(1,2))
```

---


This section looks at variability in CCF results based on windowing and SNOTEL station selection.  It requires running the "correlograms" script far enough to create the "crossdf" object.  The section on ACF generation can be skipped over.

---
```{r}
qholes <- which(is.na(crossdf$discharge))
mholes <- which(is.na(crossdf$melt))
choles <- which(is.na(crossdf$conductance))
choles
```


```{r}
plot(crossdf$discharge, type = 'l', ylab = 'discharge', main = paste('discharge at', sitename))
abline(v = qholes, col = 'red')

plot(crossdf$conductance, type = 'l', ylab = 'Conductance', main = paste('Conductance at', sitename))
abline(v = choles, col = 'red')

plot(crossdf$melt, type = 'l', ylab = 'Melt', main = paste('melt at', sitename))
abline(v = mholes, col = 'red')
```


```{r}
study.int <- c(250,420)
plot(crossdf$melt, xlim = study.int, type = 'l')
plot(crossdf$discharge, xlim = study.int, type = 'l')

par(mar = c(5,4,4,4) + 0.3)
barplot(crossdf$melt[study.int[1]:study.int[2]], ylab = 'melt (in)',
     main = paste('melt and discharge at', sitename), xlab = 'Date')
abline(v = qholes, col = 'red')
abline(v = study.int, lty =5)

par(new = T)
plot(crossdf$discharge[study.int[1]:study.int[2]], 
     type = 'l', axes = F, ylab = '', xlab = '')

axis(4, at = pretty(range(crossdf$discharge[study.int[1]:study.int[2]],na.rm = T)))
mtext("discharge (CMS)", side = 4, line = 3)
axis(1, at = seq(0,diff(study.int), length.out = 6), 
     labels = (crossdf$date[seq(study.int[1],study.int[2],length.out = 6)]))
```

```{r}
a <- study.int[1]  #index of starting time
#a <- 518
c <- 130  #window width (number of days)
b <- a+c    #calculates final index
b <- study.int[2]   #index of ending time
win1 <- c(a,300)
win2 <- c(a,360)
win3 <- c(a,b)
win4 <- c(300,b)
win5 <- c(360,b)
yrange <- c(0,max(qtc$discharge[a:b], na.rm = T))

#plot discharge over the window.  The line gets plotted later over the highlight rectangle
plot(qtc$discharge, xlim = c(a, b), ylim = yrange, type = 'n', ylab = 'discharge', 
     main = paste('discharge at', sitename), xaxt = 'n', xlab = 'date'
     )

#highlight ranges for each window of ACF analysis
rect(xleft=win1[1], xright=win1[2], ybottom = 0, ytop=.2*yrange[2],  col = linecols[1])
rect(xleft=win2[1], xright=win2[2], ybottom = .2*yrange[2], ytop=.4*yrange[2],  col = linecols[2])
rect(xleft=win3[1], xright=win3[2], ybottom = .4*yrange[2], ytop=.6*yrange[2],  col = linecols[3])
rect(xleft=win4[1], xright=win4[2], ybottom = .6*yrange[2], ytop=.8*yrange[2],  col = linecols[4])
rect(xleft=win5[1], xright=win5[2], ybottom = .8*yrange[2], ytop=1*yrange[2],  col = linecols[5])

#draw and annotate a box around any patches that exist.  Adjust numbers to position vertically
rect(patchstart, 0.5, patchend, 1.5)  #draw a box around patched section of line
text(mean(patchstart,patchend), 0.3, 'Patched values')  #annotate patch box

lines(lin.df$discharge, type = 'l', col = 'red')
lines(qtc$discharge, type = 'l')
axis(1, at = seq(a,b, length.out = 6), labels = (qtc$date[seq(a,b,length.out = 6)]))

```



UEB model cross correlegrams sensitivity.  Run "patching.rmd" and "UEB_integration.rmd" first.
---
This chunk will read in the ***_mod.csv file 
```{r}
mypath <- 'C:/Users/Daniel/Documents/Research/data/dataframes/'  #leave this as directory

#sitenames are 1:Franklin Basin, 2:Tony Grove, 3:Beaver Creek, 4:Temple Fork, 5:Right Hand Fork, 6:Ricks Spring)
i <- 1

site <- sitecodes[i]               #enter site code for file upload and export
sitename <- sitenames[i]
crossdf <- read.csv(paste0('C:/Users/Daniel/Documents/Research/data/dataframes/',site,'_mod.csv'))

crossdf$date <- as.Date(crossdf$date,'%Y-%m-%d')
head(crossdf,3)
paste('Site:', site, '-',sitename)
```

Plot conductance and discharge with data holes highlighted
```{r}
date.mark <- '03-15' #vertical blue lines will be drawn at this date for reference

qholes <- which(is.na(crossdf$qpatch))
choles <- which(is.na(crossdf$cpatch))

plot(crossdf$qpatch, type = 'l', ylab = 'discharge', main = paste('Patched discharge at', sitename))
abline(v = qholes, col = 'red')
abline(v = which(format(crossdf$date,'%m-%d')==date.mark), col='cadetblue')


plot(crossdf$cpatch, type = 'l', ylab = 'conductance', main = paste('Patched Conductance at', sitename))
abline(v = choles, col = 'red')
abline(v = which(format(crossdf$date,'%m-%d')==date.mark), col='cadetblue')

```

Select a specific study interval
```{r}
study.int <- c(230,483)
yrange <- c(0,max(crossdf$qpatch[study.int[1]:study.int[2]], na.rm = T))

plot(crossdf$qpatch, xlim = study.int, ylim = yrange, type = 'l', ylab = 'discharge', 
     main = paste('discharge at', sitename)
     )
abline(v = qholes, col = 'red')

```

```{r}
which(crossdf$wyday==1)
```



```{r}
a <- study.int[1]  #index of starting time

b <- study.int[2]   #index of ending time based on study interval
win1 <- c(a,a+205)  #red rect
win2 <- c(a+40,a+220)  #yellow rect
win3 <- c(a+40,a+205)  #green rect
win4 <- c(a+0,a+220)   #gray rect
win5 <- c(a,b)    #blue rect

barplot(crossdf$SWIT[study.int[1]:study.int[2]], axes = F)
axis(side = 4, at = pretty(range(crossdf$SWIT[a:b]), n = 2))

par(new=T)
#plot discharge over the window.  The line gets plotted later over the highlight rectangles
plot(crossdf$qpatch, xlim = c(a, b), ylim = yrange, type = 'n', ylab = 'discharge', 
     main = paste('discharge at', sitename,crossdf$WY[a]), xaxt = 'n', xlab = 'date'
     )

#highlight ranges for each window of CCF analysis
rect(xleft=win1[1], xright=win1[2], ybottom = 0, ytop=.2*yrange[2], border = NA,  
     col = rgb(rgbmat[1,1],rgbmat[2,1],rgbmat[3,1], alpha = 0.5))
rect(xleft=win2[1], xright=win2[2], ybottom = .2*yrange[2], ytop=.4*yrange[2], border = NA,  
     col = rgb(rgbmat[1,2],rgbmat[2,2],rgbmat[3,2], alpha = 0.5))
rect(xleft=win3[1], xright=win3[2], ybottom = .4*yrange[2], ytop=.6*yrange[2], border = NA,  
     col = rgb(rgbmat[1,3],rgbmat[2,3],rgbmat[3,3], alpha = 0.5))
rect(xleft=win4[1], xright=win4[2], ybottom = .6*yrange[2], ytop=.8*yrange[2], border = NA,  
     col = rgb(rgbmat[1,4],rgbmat[2,4],rgbmat[3,4], alpha = 0.5))
rect(xleft=win5[1], xright=win5[2], ybottom = .8*yrange[2], ytop=1*yrange[2],  border = NA, 
     col = rgb(rgbmat[1,5],rgbmat[2,5],rgbmat[3,5], alpha = 0.5))

#

lines(crossdf$qpatch, type = 'l')
axis(1, at = seq(a,b, length.out = 6), labels = (crossdf$date[seq(a,b,length.out = 6)]))

```

Name each window for the legend on the CCF plot, in order from bottom to top with the window highlight rectangles shown above 
```{r}
#automatically enters date ranges to the legend for each window
win.names <- c(paste(crossdf$day[win1[1]], 'to', crossdf$day[win1[2]]),
               paste(crossdf$day[win2[1]], 'to', crossdf$day[win2[2]]), 
               paste(crossdf$day[win3[1]], 'to', crossdf$day[win3[2]]),
               paste(crossdf$day[win4[1]], 'to', crossdf$day[win4[2]]),
               paste(crossdf$day[win5[1]], 'to', crossdf$day[win5[2]]))


#win.names <- c('3/5-8/12','4/4-10/11','4/4-8/12','3/5-10/11','4/4-11/10')
```


Compute CCF of Q | SWIT within each window.
```{r}
lagmax <- 200
ccf1 <- ccf(crossdf$qpatch[win1[1]:win1[2]], crossdf$SWIT[win1[1]:win1[2]], lag.max = lagmax, 
             plot = F, na.action = na.pass)
ccf2 <- ccf(crossdf$qpatch[win2[1]:win2[2]], crossdf$SWIT[win2[1]:win2[2]], lag.max = lagmax, 
             plot = F, na.action = na.pass)
ccf3 <- ccf(crossdf$qpatch[win3[1]:win3[2]], crossdf$SWIT[win3[1]:win3[2]], lag.max = lagmax, 
             plot = F, na.action = na.pass)
ccf4 <- ccf(crossdf$qpatch[win4[1]:win4[2]], crossdf$SWIT[win4[1]:win4[2]], lag.max = lagmax, 
             plot = F, na.action = na.pass)
ccf5 <- ccf(crossdf$qpatch[win5[1]:win5[2]], crossdf$SWIT[win5[1]:win5[2]], lag.max = lagmax, 
             plot = F, na.action = na.pass)

```

```{r}
plot(ccf1$lag, ccf1$acf, type = 'l', col=linecols[1],
     ylab = 'Correlation', xlab = 'Lag (days)', ylim = c(-0.2,0.9), xlim = c(0,50), 
     main = paste('Q|SWIT Crosscorrelation window sensitivity:', sitename, crossdf$WY[a]))
lines(ccf2$acf[(lagmax+2):(lagmax*2+1)], col = linecols[2],xlim = c(0,lagmax))
lines(ccf3$acf[(lagmax+2):(lagmax*2+1)], col = linecols[3],xlim = c(0,lagmax))
lines(ccf4$acf[(lagmax+2):(lagmax*2+1)], col = linecols[4])
lines(ccf5$acf[(lagmax+2):(lagmax*2+1)], col = linecols[5])

abline(h = 0.2, lty = 3)
abline(h = -0.2, lty = 3)

legend('bottomleft', legend = win.names, lty = 1, col = linecols[1:5]) 
```






