---
title: "SNOTEL"
author: "Daniel Thurber"
date: "5/6/2021"
output: pdf_document
---

Input the name of the file within the designated folder and enter initialization values.
```{r}
library(naniar)
library(ggplot2)
mypath <- 'C:/Users/Daniel/Documents/Research/data/SNOTEL/'
site <- 'FB_484'
#FB_484, GCS_1114, KN_1115, TF_1013, TGL_823, TGRS_1113, UDD_1098
sitesnotel <- c(1115, 1115, 1114,1013,1013, 823, 
              1013, 1098, 1113, 1113, 823,1098)
csitename <- "Franklin Basin" #common name for plots
```


generate dataframe from .csv
```{r}
snofile <- paste0(site,'.csv')
snodf <- read.csv(paste0(mypath,snofile), stringsAsFactors = F)
```

Add water year, melt, and rain to dataframe
```{r}
snodf$Date = as.Date(snodf$Date, format = "%m/%d/%Y")

snodf$WY = ifelse(as.numeric(format(snodf$Date,'%m'))>=10, 
                     as.numeric(format(snodf$Date,'%Y'))+1, 
                     as.numeric(format(snodf$Date,'%Y'))) #determine water year
```

Calculate daily melt and rain columns
```{r}
snodf$melt = 0
for (i in 1:nrow(snodf)){ #calculate and report daily melt
  snodf$melt[i] = max(0,snodf$SWE_in[i-1]-snodf$SWE_in[i]) 
}
snodf$rain=0
for (i in 1:nrow(snodf)){ #calculate and report daily rain
  snodf$rain[i] = round(max(0,snodf$precip_incre_in[i]-max(0,snodf$SWE_in[i+1]+snodf$SWE_in[i])),2) 
}
```



```{r}
WaterYear <- 2018
startday <- 190
endday <- 320
```

Create dataframe for the water year of interest
```{r}
wydf <- data.frame(snodf[which(snodf$WY==WaterYear),])
wydf$discharge=NA

```



Show SWE and surface water input together on the same plot
```{r}
par(mar = c(5,4,4,4) + 0.3)
plot(wydf$SWE_in,
     xlab="WY day", ylab = 'SWE (in)',
     main = paste("SWE and surface water input at",csitename, 'for', WaterYear),
     type = 'l')
legend(5,28, legend = c('SWE', 'Melt', 'Rain'), 
       lty = 1, col = c('black', 'cadetblue3', 'red3'))
par(new = T)
plot(wydf$melt, 
     xlab = '', ylab = '', type = 'l', axes = F,
     col = 'cadetblue3')
lines(wydf$rain, 
     xlab = '', ylab = '',
     col="red3")
axis(side = 4, at = pretty(range(wydf$melt)))      # Add second axis
mtext("surface water input (in/day)", side = 4, line = 3) 
#lines(wydf$melt, xlab = '', ylab = '',
#      col = 'cadetblue3')
```

```{r}
write.csv(snodf, paste0('C:/Users/Daniel/Documents/Research/data/dataframes/',site,'.csv'), row.names = F)
```

--- Experimental code for plotting discharge and SWI
Incorporate discharge data if desired
```{r}
for (i in 1:nrow(dailyq)){ #this relies on the construction of the dailyq dataframe
  wydf$discharge[which(wydf$Date==dailyq$date[i])] = dailyq$discharge[i] 
}
```


plot surface water input with discharge
```{r}
par(mar = c(5,4,4,4) + 0.3)
plot(wydf$discharge[startday:endday],
     xlab="WY day", ylab = 'Discharge (CMS)',
     main = paste("discharge and surface water input at",sitename, 'for', WaterYear),
     type = 'l')
legend("topright", legend = c('discharge', 'Melt', 'Rain'), 
       lty = 1, col = c('black', 'cadetblue3', 'red3'))
par(new = T)
plot(wydf$melt[startday:endday], 
     xlab = '', ylab = '', type = 'l', axes = F,
     col = 'cadetblue3')
lines(wydf$rain[startday:endday], 
     xlab = '', ylab = '',
     col="red3")
axis(side = 4, at = pretty(range(wydf$melt)))      # Add second axis
mtext("surface water input (in/day)", side = 4, line = 3) 
#lines(wydf$melt, xlab = '', ylab = '',
#      col = 'cadetblue3')
```



