---
title: "UEB Integration"
author: "Daniel Thurber"
date: "7/29/2021"
output: pdf_document
---
Input the name of the file within the designated folder and enter initialization values.


```{r}
library(naniar)
library(ggplot2)
switpath <- 'C:/Users/Daniel/Documents/Research/data/UEB_outputs/'
patchpath <- 'C:/Users/Daniel/Documents/Research/data/dataframes/patched_data/'

sitecodes <- c('LR_FB_BA', 'LR_TG_BA', 'BC_CONF_A', 'TF_CONF_A','RHF_CONF_A', 'RS_CONF_A', 
               'TF_SAWM_A', 'SPC_CONF_A', 'LR_WC_A', 'LR_GCB_A', 'WCS_CONF_A', 'LR_FD')
sitenames <- c('Franklin Basin', 'Tony Grove', 'Beaver Creek', 'Temple Fork', 'Right Hand Fork','Ricks Spring', 
               'TF at Sawmill', 'Spawn Creek', 'Above Wood Camp', 'Guinavah Campground','Wood Camp Spring','First Dam')
siteabbr <- c('FB', 'TG', 'BC', 'TF','RH', 'RS', 
              'TS', 'SC', 'WC', 'GC', 'WS','FD')

sitesnotel <- c(1115, 1115, 1114,1013,1013, 823, 
              1013, 1098, 1113, 1113, 823,1098)
ST.el <- c(7250, 7250, 7705,7406,7406, 8474, 
           7406, 8270, 6332, 6332, 8474,8270)*0.3048

#FB_484, GCS_1114, KN_1115, TF_1013, TGL_823, TGRS_1113, UDD_1098
#GCS: 7705, KN: 7250, TF: 7406, USUDD: 8270, TGRS: 6332, TGL: 8474, FB: 8140

startyear <- c(2015,2015,2016,2016,2017,2016,
               2019,2019,2019,2019,2019,2015)
acf.sites <- c('FB_', 'TG_', 'BC_', 'TF_', 'RH_', 'RS_', 'TS_', 'SC_', 'WC_', 'GC_', 'WS_', 'FD_')
acf.years <- c('15','16','17','18','19','20','21')
plot.points <- c(1,5,7,8,15,17,19)

linecols <- c('brown3', 'goldenrod', 'forestgreen', 'bisque4', 'slateblue', 'tan1', 
              'aquamarine3', 'magenta4', 'sienna3','cyan','violetred2','yellow2')
linetypes <- c(1,1,1,1,1,3,1,1,1,1,4,1)
rgbmat <- col2rgb(linecols)
wydates <- data.frame(wyday = seq(1,366),
day=format(seq.Date(as.Date('2019-10-1','%Y-%m-%d'),as.Date('2020-09-30','%Y-%m-%d'),1),'%m-%d'))
comp.df <- read.csv(paste0('C:/Users/Daniel/Documents/Research/data/dataframes/catchment_comparison.csv'))
corr.df <- read.csv('C:/Users/Daniel/Documents/Research/data/dataframes/correlograms.csv')
colnames(comp.df)[4:171] <- str_sub(colnames(comp.df)[4:171],-6,-1) #make sure column names are only the last 6 characters
row.names(comp.df) <- sitecodes

```
```{r}
i <-12     #enter site INDEX for file upload and export

site <- sitecodes[i]               
sitename <- sitenames[i]
siteabv <- siteabbr[i]
sitenum <- i
paste(sitename, site)
```


Read the patched data csv into a dataframe

```{r}
qtc <- read.csv(paste0(patchpath,site,'_patched.csv'), stringsAsFactors = F)
```


format 'date' as a date and generate day column without year, then check the data formats. 
```{r}

qtc$date <- as.Date(qtc$date,'%Y-%m-%d')
qtc$day <- format(as.Date(qtc$date),'%m-%d')
qtc$wyday <- 0
head(qtc,3)
```




Populate water year day column with appropriate values 1-366
```{r}
for (i in 1:nrow(qtc)){
  qtc$wyday[i] <- wydates$wyday[which(wydates$day==qtc$day[i])]
}
```

Read the UEB model results into dataframes.  Each column represents a separate water year
```{r}
swit.df <- read.csv(paste0(switpath,site,'_SWIT.csv'), stringsAsFactors = F, header = F)
swe.df <- read.csv(paste0(switpath,site,'_SWE.csv'), stringsAsFactors = F, header = F)

```

Create a new dataframe for model results with all output values stacked in the same column
```{r}
mod.df <- data.frame(date =  seq.Date(as.Date('1980-10-1','%Y-%m-%d'), as.Date('2018-09-30','%Y-%m-%d'),1))
mod.df$SWIT <- na.omit(stack(swit.df)$values)
mod.df$SWE <- na.omit(stack(swe.df)$values)
#if error: replacement has 13908 rows (should be 13879), replace zeroes in row 366 with NA
```

Merge dataframes for future cross-correlation.  Only keep rows within the period of record for Q and SC and predicted by UEB model.
```{r}
mod.df <- merge(mod.df, qtc, by = 'date')
```



```{r}
plot(mod.df$cpatch, type = 'l', col = 'red', 
     xlim = c(1,nrow(mod.df)), ylim = range(mod.df$cpatch,na.rm=F))
lines(qtc$cpatch)
plot(mod.df$qpatch, type = 'l', col = 'red', 
     xlim = c(1,nrow(qtc)))
lines(qtc$qpatch)
```


```{r}
write.csv(mod.df, paste0('C:/Users/Daniel/Documents/Research/data/dataframes/',site,'_mod.csv'), row.names = F)
```


