---
title: "LRO Aggregate"
author: "Daniel Thurber"
date: "2/22/2021"
output: pdf_document
---

Input the name of the file within the designated folder and read the csv into a dataframe.
```{r}
library(naniar)
library(ggplot2)
mypath <- 'C:/Users/Daniel/Documents/Research/data/LRO_aquatic/' #leave this directory alone!
#LR_FB_BA, BC_CONF_A, LR_TG_BA, TF_CONF_A, RHF_CONF_A
site <- 'RS_CONF_A'               #enter site code for file upload and export
sitename <- 'Ricks Spring'        #enter site name for plotting
minQ <- 0.01                    #below these thresholds, values will be replaced with NA
minT <- .001
minC <- .001
```

Open all files and save as dataframes.
```{r}

qfile <- paste0(site,'_Q.csv')
qdf <- read.csv(paste0(mypath,qfile), stringsAsFactors = F)
tfile <-  paste0(site,'_T.csv')
tdf <- read.csv(paste0(mypath,tfile), stringsAsFactors = F)
cfile <-  paste0(site,'_SC.csv')
cdf <- read.csv(paste0(mypath,cfile), stringsAsFactors = F)
```

then check the data format. 
```{r}
head(qdf,3)
```




Find the first date where data was collected.
```{r}
qstart <- as.Date(qdf$DateTime[1], '%m / %d / %Y %H:%M')
qstart
cstart <- as.Date(cdf$DateTime[1], '%m / %d / %Y %H:%M')
cstart
tstart <- as.Date(tdf$DateTime[1], '%m / %d / %Y %H:%M')
tstart
mindate <- min(qstart,cstart,tstart)
mindate
```


Add column for date and discharge/conductance/temperature, replace all low values with NA
```{r}
minQ <- 0.100                     #below these thresholds, values will be replaced with NA
minT <- .001
minC <- .001
qdf$date <- as.Date(qdf$DateTime, '%m / %d / %Y %H:%M')
qdf$discharge <- (as.numeric(qdf$Value))
qdf$discharge <- replace(qdf$discharge, qdf$discharge<minQ, NA)


cdf$date <- as.Date(cdf$DateTime, '%m / %d / %Y %H:%M')
cdf$conductance <- (as.numeric(cdf$Value))
cdf$conductance <- replace(cdf$conductance, cdf$conductance<minC, NA)


tdf$date <- as.Date(tdf$DateTime, '%m / %d / %Y %H:%M')
tdf$temperature <- (as.numeric(tdf$Value))
tdf$temperature <- replace(tdf$temperature, tdf$temperature<minT, NA)


#qdf$WY = ifelse(qdf$month>=10, qdf$Year+1, qdf$Year) #determine water year
```

Plot each time series to see if any extreme values need to be addressed
```{r}
plot(qdf$discharge, type = "l", ylim = c(0,10))
plot(cdf$conductance~cdf$date, type = "l", xlab = "Date", ylab = "Specific Conductance")
plot(tdf$temperature, type = "l", ylim = c(0,10))
```


Calculate daily mean for each variable
```{r}
dailyq <- aggregate(discharge~date, qdf, FUN = "mean")

dailyt <- aggregate(temperature~date, tdf, FUN = "mean")

dailyc <- aggregate(conductance~date, cdf, FUN = "mean")

```


merge dataframes for all overlapping values
```{r}
QTCdf <- merge(dailyc, dailyq, by = 'date')
QTCdf <- merge(QTCdf, dailyt, by = 'date')
```

Add a water year column to the dataframe
```{r}
QTCdf$WY = ifelse(as.numeric(format(QTCdf$date,'%m'))>=10, 
                     as.numeric(format(QTCdf$date,'%Y'))+1, 
                     as.numeric(format(QTCdf$date,'%Y'))) #determine water year
```

Plot all time series and look for any issues worth addressing
```{r}
day1 <- 1
#day1 <- 600 #use these values to zoom in on a specific date range
dayend <- nrow(QTCdf)
#dayend <- 680  #comment them out to return to full period of record
plot(QTCdf$date[day1:dayend],QTCdf$discharge[day1:dayend], type = 'l', col = 'cadetblue4',
     xlab = "date", ylab = "discharge (CMS)", main = paste("discharge at ", sitename))

plot(QTCdf$date[day1:dayend],QTCdf$temperature[day1:dayend], type = 'l', col = 'cadetblue4',
     xlab = "date", ylab = "temperature (C)", main = paste("temperature at ", sitename))

plot(QTCdf$date[day1:dayend],QTCdf$conductance[day1:dayend], type = 'l', col = 'cadetblue4',
     xlab = "date", ylab = "conductance ", main = paste("conductance at ", sitename))
day1 <- 1
dayend <- nrow(QTCdf)
```



```{r}
write.csv(QTCdf, paste0('C:/Users/Daniel/Documents/Research/data/dataframes/',site,'.csv'), row.names = F)
```





